### 2019-11-11 PaperDraft.Rmd

---
title: "Draft"
author: " "
date: "November 11, 2019"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

### Motivation

- Explination of Game, Set, Match

### Methods

- Where we got our data

- Probability of winning a game, set, match

### Reproducability

### Extension

### 2019-12-05 funs.R
Probability of winning a match

@@ -55,3 +55,14 @@ ps <- pASij(7,5, pag, pbg) + pAT(6,6,pag, pbg) + sapply(0:4, pASij, i=6, pAG=pag
 #where pag is prob A wins a game given A served and 
 #pbg is prob B wins a game given B served
 #still need to write pAT
+
+
+## The probability of winning two out of three sets, resulting in winning a match
+pM=function(ps_a, ps_b,num_set){
+  if (num_sets==2){
+    (ps_a)^2+2*(ps_a)^2*ps_b
+  }
+  if(num_sets==3){
+    (ps_a)^3+3*(ps_a)^3*ps_b+6*ps_a^3*ps_b^2
+  }
+}

### 2019-12-07 funs.R
Added Tie Breaker Function

@@ -19,7 +19,7 @@ pg <- function(pr) {
 
 #equation 6-8
 pASij <- function(i, j, pAG, pBG){ #i , j , prob a wins given a served, prob b wins given b served
-  if(i == 0 & j == 1){return(1)}
+  if(i == 0 & j == 0){return(1)}
   if(i < 0){return(0)}
   if(j < 0){return(0)}
   for( a in 1:i){ 
@@ -50,8 +50,49 @@ pASij <- function(i, j, pAG, pBG){ #i , j , prob a wins given a served, prob b w
   }
   
 }
+
+
+
+pATij <- function(i, j, pAR, pBR){ #i , j , prob a wins given a served, prob b wins given b served
+  if(i == 0 & j == 0){return(1)}
+  if(i < 0){return(0)}
+  if(j < 0){return(0)}
+  for( a in 0:i){ 
+    for( b in j:7){
+      MO <- mod(i+j-1, 4)
+      if(MO == 0 | MO == 3) {
+        if(j == 7 & i <= 6){
+          return(pATij(i-1, j, pAR, pBR)*(pAR))
+        }
+        else if( i == 7 & j <= 6){
+          return(pATij(i, j-1, pAR, pBR)*(1-pAR))
+        }
+        else{
+          return(pATij(i-1, j, pAR, pBR)*pAR + pATij(i, j-1, pAR, pBR)*(1-pAR))
+        }
+      }
+      else{
+        if(j == 7 & i <= 6){
+          return(pATij(i-1, j, pAR, pBR)*(1-pBR))
+        }
+        else if( i == 7 & j <= 6){
+          return(pATij(i, j-1, pAR, pBR)*(pBR))
+        }
+        else{
+          return(pATij(i-1, j, pAR, pBR)*(1-pBR) + pATij(i, j-1, pAR, pBR)*(pBR))
+        }
+      }
+    }
+  }
+  
+}
+
+
+
+
+
 #Prob A wins a set given a served 
-ps <- pASij(7,5, pag, pbg) + pAT(6,6,pag, pbg) + sapply(0:4, pASij, i=6, pAG=pag, pBG=pbg )
+ps <- pASij(7,5, pag, pbg) + pATij(6,6,pag, pbg) + sum(sapply(0:4, pASij, i=6, pAG=pag, pBG=pbg ))
 #where pag is prob A wins a game given A served and 
 #pbg is prob B wins a game given B served
 #still need to write pAT

### 2019-12-07 funs.R
Add prob a wins a set

@@ -92,7 +92,15 @@ pATij <- function(i, j, pAR, pBR){ #i , j , prob a wins given a served, prob b w
 
 
 #Prob A wins a set given a served 
-ps <- pASij(7,5, pag, pbg) + pATij(6,6,pag, pbg) + sum(sapply(0:4, pASij, i=6, pAG=pag, pBG=pbg ))
+ps <- function(pag, pbg){
+  ret <- pASij(7,5, pag, pbg) + pATij(6,6,pag, pbg) + sum(sapply(0:4, pASij, i=6, pAG=pag, pBG=pbg ))
+  if(ret > 1){return(1)}
+  else {return(ret)}
+}
+
+
+
+
 #where pag is prob A wins a game given A served and 
 #pbg is prob B wins a game given B served
 #still need to write pAT

### 2019-12-07 Group1Prez.Rmd
Start Prez

---
title: "Group 1: Tennis "
author: "Olivia Beck, Emma Wilson, Ryan Volkert"
date: "December 12, 2019"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## The Game of Tennis

Points – Smallest unit of measurement. Points increment from Love(0)-15-30-40-game.
Games – Games consist of 4 points each, and is won when a player reaches 4 points with at least a 2 point advantage.
Sets – A set consists of 6 games and is won by the player/team who reaches 6 games first with least a 2 point lead.
Advantage Set – If a game score of 6-6 is reached and advantage set rules are used, a player/team can only win a set with a 2 game lead.
Matches – A match is usually played as best of 3 or best of 5 sets.
Deuce – Occurs if a score of 40-40 is reached. In order to win the game, a player/team must win 2 consecutive points in order to take the game. If a player wins one point, they have advantage, but if they lose the next point, the score returns to deuce.
Tie-break game – If a game score of 6-6 is reached and tie-break set rules are used, players must play a tie-break game in order to decide who wins the set. In a tie-break game, a player/team must reach 7 points with a two point advantage to win. For the serving format of a tie-break game, player 1 serves for the first point, player 2 serves for the next two points, player 1 serves for the next two points after that, etc.

## Slide with Bullets

- Bullet 1
- Bullet 2
- Bullet 3

## Slide with R Output

```{r cars, echo = TRUE}
summary(cars)
```

## Slide with Plot

```{r pressure}
plot(pressure)
```

### 2019-12-07 funs.R
Prob of winning tourney

@@ -103,15 +103,37 @@ ps <- function(pag, pbg){
 
 #where pag is prob A wins a game given A served and 
 #pbg is prob B wins a game given B served
-#still need to write pAT
-
 
 ## The probability of winning two out of three sets, resulting in winning a match
-pM=function(ps_a, ps_b,num_set){
-  if (num_sets==2){
+pM <- function(ps_a, ps_b,num_set){
+  if (num_set==2){
     (ps_a)^2+2*(ps_a)^2*ps_b
   }
-  if(num_sets==3){
+  if(num_set==3){
     (ps_a)^3+3*(ps_a)^3*ps_b+6*ps_a^3*ps_b^2
   }
+}
+
+# Probability of winning a tournament
+pTC <- function(ps_1, ps_2, ps_3, ps_4, numset) {
+  p12 <- pM(ps_1, ps_2, numset)
+  p13 <- pM(ps_1, ps_3, numset)
+  p14 <- pM(ps_1, ps_4, numset)
+  
+  p21 <- 1 - p12
+  p23 <- pM(ps_2, ps_3, numset)
+  p24 <- pM(ps_2, ps_4, numset)
+  
+  p31 <- 1 - p13
+  p32 <- 1 - p23
+  p34 <- pM(ps_3, ps_4, numset)
+  
+  p41 <- 1 - p14
+  p42 <- 1 - p24
+  p43 <- 1 - p34
+  
+  c(p12 * (p13*p34 + p14*p43),
+    p21 * (p23*p34 + p24*p43),
+    p34 * (p31*p12 + p32*p21),
+    p43 * (p41*p12 + p42*p21))
 }

### 2019-12-07 Group1Prez.Rmd
update

@@
 
-Points – Smallest unit of measurement. Points increment from Love(0)-15-30-40-game.
-Games – Games consist of 4 points each, and is won when a player reaches 4 points with at least a 2 point advantage.
-Sets – A set consists of 6 games and is won by the player/team who reaches 6 games first with least a 2 point lead.
-Advantage Set – If a game score of 6-6 is reached and advantage set rules are used, a player/team can only win a set with a 2 game lead.
-Matches – A match is usually played as best of 3 or best of 5 sets.
-Deuce – Occurs if a score of 40-40 is reached.
-In order to win the game, a player/team must win 2 consecutive points in order to take the game.
-If a player wins one point, they have advantage, but if they lose the next point, the score returns to deuce.
-Tie-break game – If a game score of 6-6 is reached and tie-break set rules are used, players must play a tie-break game in order to decide who wins the set.
-In a tie-break game, a player/team must reach 7 points with a two point advantage to win.
-For the serving format of a tie-break game, player 1 serves for the first point, player 2 serves for the next two points, player 1 serves for the next two points after that, etc.
+- Point: Smallest unit of measurement (Love-15-30-40-game)
 
-## Slide with Bullets
+- Game: A game is one when a player reaches 4 points with at least a 2 point advantage
 
-- Bullet 1
-- Bullet 2
-- Bullet 3
+- Set: A set consists of 6 games and is won by the player who reaches 6 games first
+
+- Advantage Set: If a game score of 6-6 is reached and advantage set rules are used, a player can only win a set with a 2 game lead
+
+- Matches: Best of 3 set (for women) or 5 sets (for men)
+
+- Tie-break game: If a game score of 6-6 is reached and tie-break set rules are used. In a tie-break game, a player/team must reach 7 points with a two point advantage to win
+
+## Values
+
+Things we need to know:
+
+- Empirical probability of winning a rally on serve
+
+- Empirical probability of winning a game on serve  \pause
+
+Things we need to calculate:
+
+- Theoretical probability of winning a game on serve
+
+- Theoretical probability of winning a set
+
+- Theoretical probability of winning a match
+
+- Theoretical probability of winning the tie-breaker
 
@@
 
-```{r cars, echo = TRUE}
-summary(cars)
+```{r, echo = TRUE}
+
 ```

### 2019-12-07 funs.R

@@ -13,7 +13,7 @@ pr <- function(pwon, pserve) {
 pg <- function(pr) {
   qr <- 1 - pr
   
-  pr^4 * (1 + 4*qr + 10*qr^2) + 10*(pr*qr)^3 * pr^2 * (1 - 2*p2*qr)^-1
+  pr^4 * (1 + 4*qr + 10*qr^2) + 20*(pr*qr)^3 * pr^2 * (1 - 2*pr*qr)^-1
 }
 
 

### 2019-12-07 funs.R
update

@@ -107,7 +107,7 @@ ps <- function(pag, pbg){
 
 
 ## The probability of winning two out of three sets, resulting in winning a match
-pM=function(ps_a, ps_b,num_set){
+pM <- function(ps_a, ps_b,num_set){
   if (num_sets==2){
     (ps_a)^2+2*(ps_a)^2*ps_b
   }

### 2019-12-07 funs.R
Fixed pM function

@@ -110,7 +110,7 @@ pM <- function(ps_a, ps_b,num_set){
     ret<- (ps_a)^2+2*(ps_a)^2*(1-ps_b)
   }
   if(num_set==3){
-    ret <- (ps_a)^3+3*(ps_a)^3*ps_b+6*ps_a^3*(1-ps_b)^2
+    ret <- (ps_a)^3+3*(ps_a)^3*(1-ps_b)+6*ps_a^3*(1-ps_b)^2
   }
   
   if(ret>1){return(1)}
@@ -140,3 +140,20 @@ pTC <- function(ps_1, ps_2, ps_3, ps_4, numset) {
     p34 * (p31*p12 + p32*p21),
     p43 * (p41*p12 + p42*p21))
 }
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+
+

### 2019-12-07 Group1Prez.Rmd
Update Prez

@@
 
-```{r setup, include=FALSE}
+```{r setup, include=FALSE, warning=FALSE}
 knitr::opts_chunk$set(echo = FALSE)
+source("funs.R")
+library(knitr)
+library(kableExtra)
+library(tidyverse)
+set.seed(400)
 ```
@@
 
-```{r, echo = TRUE}
+```{r, echo = FALSE}
+
+TDWomen <- as.data.frame(matrix(0, nrow = 4, ncol = 3))
+
+colnames(TDWomen) <- c("P(Win a Rally)", "Empirical P(Win a Game)", "Paper P(Win a Game)" )
+
+TDWomen[1, ] <- c(0.69, 0.71, 0.89)
+TDWomen[2, ] <- c(0.63, 0.80, 0.79)
+TDWomen[3, ] <- c(0.65, 0.85, 0.83)
+TDWomen[4, ] <- c(0.63, 0.77, 0.79)
+
+OurDatWomen <- as.matrix(round(c(pg(TDWomen[1,1]), pg(TDWomen[2,1]), pg(TDWomen[3,1]), pg(TDWomen[4,1])),2))
+
+TDWomen$`Our P(Win a Game)` <-(OurDatWomen)
+
+kable(TDWomen, format = "latex", booktabs = TRUE)%>%
+          kable_styling(latex_options = "scale_down")
 

### 2019-12-07 Group1Prez.tex
Update Prez

\documentclass[ignorenonframetext,]{beamer}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\usepackage{fixltx2e} % provides \textsubscript
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
\else % if luatex or xelatex
  \ifxetex
    \usepackage{mathspec}
  \else
    \usepackage{fontspec}
  \fi
  \defaultfontfeatures{Ligatures=TeX,Scale=MatchLowercase}
\fi
% use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
% use microtype if available
\IfFileExists{microtype.sty}{%
\usepackage{microtype}
\UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\newif\ifbibliography
\hypersetup{
            pdftitle={Group 1: Tennis},
            pdfauthor={Olivia Beck, Emma Wilson, Ryan Volkert},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight0.8\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}

% Prevent slide breaks in the middle of a paragraph:
\widowpenalties 1 10000
\raggedbottom

\AtBeginPart{
  \let\insertpartnumber\relax
  \let\partname\relax
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \let\insertsectionnumber\relax
    \let\sectionname\relax
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \let\insertsubsectionnumber\relax
  \let\subsectionname\relax
  \frame{\subsectionpage}
}

\setlength{\parindent}{0pt}
\setlength{\parskip}{6pt plus 2pt minus 1pt}
\setlength{\emergencystretch}{3em}  % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{0}

\title{Group 1: Tennis}
\author{Olivia Beck, Emma Wilson, Ryan Volkert}
\date{December 12, 2019}

\begin{document}
\frame{\titlepage}

\begin{frame}{The Game of Tennis}

\begin{itemize}
\item
  Point: Smallest unit of measurement (Love-15-30-40-game)
\item
  Game: A game is one when a player reaches 4 points with at least a 2
  point advantage
\item
  Set: A set consists of 6 games and is won by the player who reaches 6
  games first
\item
  Advantage Set: If a game score of 6-6 is reached and advantage set
  rules are used, a player can only win a set with a 2 game lead
\item
  Matches: Best of 3 set (for women) or 5 sets (for men)
\item
  Tie-break game: If a game score of 6-6 is reached and tie-break set
  rules are used. In a tie-break game, a player/team must reach 7 points
  with a two point advantage to win
\end{itemize}

\end{frame}

\begin{frame}{Values}

Things we need to know:

\begin{itemize}
\item
  Empirical probability of winning a rally on serve
\item
  Empirical probability of winning a game on serve \pause
\end{itemize}

Things we need to calculate:

\begin{itemize}
\item
  Theoretical probability of winning a game on serve
\item
  Theoretical probability of winning a set
\item
  Theoretical probability of winning a match
\item
  Theoretical probability of winning the tie-breaker
\end{itemize}

\end{frame}

\begin{frame}{Slide with R Output}

\begin{table}[H]
\centering
\resizebox{\linewidth}{!}{
\begin{tabular}{rrrr}
\toprule
P(Win a Rally) & Empirical P(Win a Game) & Paper P(Win a Game) & Our P(Win a Game)\\
\midrule
0.69 & 0.71 & 0.89 & 0.89\\
0.63 & 0.80 & 0.79 & 0.79\\
0.65 & 0.85 & 0.83 & 0.83\\
0.63 & 0.77 & 0.79 & 0.79\\
\bottomrule
\end{tabular}}
\end{table}

\end{frame}

\begin{frame}{Slide with Plot}

\includegraphics{Group1Prez_files/figure-beamer/pressure-1.pdf}

\end{frame}

\end{document}

### 2019-12-07 Group1Prez.Rmd
Finally Got Table working

@@
 output: beamer_presentation
+header-includes: 
+  - \usepackage{booktabs} 
+  - \usepackage{longtable} 
+  - \usepackage{array} 
+  - \usepackage{multirow} 
+  - \usepackage{wrapfig} 
+  - \usepackage{float} 
+  - \usepackage{colortbl} 
+  - \usepackage{pdflscape} 
+  - \usepackage{tabu} 
+  - \usepackage{threeparttable} 
+  - \usepackage{threeparttablex} 
+  - \usepackage[normalem]{ulem} 
+  - \usepackage{makecell} 
+  - \usepackage{xcolor}
+
 ---
@@
 library(knitr)
+options(kableExtra.latex.load_packages = FALSE) 
 library(kableExtra)

### 2019-12-10 funs.R
Updated pTC

@@ -1,5 +1,6 @@
 
 library(numbers)
+library(tidyverse)
 
 
 # Probability that A wins rally given A serves
@@ -105,38 +106,66 @@ ps <- function(pag, pbg){
 #pbg is prob B wins a game given B served
 
 ## The probability of winning two out of three sets, resulting in winning a match
-pM <- function(ps_a, ps_b,num_set){
+pM <- function(ps_a, ps_b, num_set){
   if (num_set==2){
-    ret<- (ps_a)^2+2*(ps_a)^2*(1-ps_b)
+    ret <- (ps_a)^2 + 2*(ps_a)^2 * ps_b
   }
   if(num_set==3){
-    ret <- (ps_a)^3+3*(ps_a)^3*ps_b+6*ps_a^3*(1-ps_b)^2
+    ret <- (ps_a)^3 + 3*(ps_a)^3 * ps_b + 6*ps_a^3 * (ps_b)^2
   }
   
-  if(ret>1){return(1)}
+  if(ret>1) return(1)
   return(ret)
 }
 
 # Probability of winning a tournament
-pTC <- function(ps_1, ps_2, ps_3, ps_4, numset) {
-  p12 <- pM(ps_1, ps_2, numset)
-  p13 <- pM(ps_1, ps_3, numset)
-  p14 <- pM(ps_1, ps_4, numset)
+pTC <- function(pr_1, pr_2, pr_3, pr_4, numset) {
+  tourney <- data.frame(Player = 1:4,
+                       pRally = c(pr_1,
+                                  pr_2,
+                                  pr_3,
+                                  pr_4),
+                       pGame = NA,
+                       pTourney = NA) %>%
+    mutate(pGame = pg(pRally))
   
-  p21 <- 1 - p12
-  p23 <- pM(ps_2, ps_3, numset)
-  p24 <- pM(ps_2, ps_4, numset)
+  pSet <- matrix(NA, nrow=4, ncol=4)
   
-  p31 <- 1 - p13
+  for(i in 1:4) {
+    for(j in 1:4) {
+      if(i==j) pSet[i,j] <- 0
+      else pSet[i,j] <- ps(tourney$pGame[i], tourney$pGame[j])
+    }
+  }
+  
+  semi <- matrix(NA, nrow=4, ncol=4)
+  
+  for(i in 1:4) {
[…]

### 2019-12-10 Group1Prez.Rmd
Update Presentation

@@
 
+- Theoretical probability of winning the tie-breaker
+
 - Theoretical probability of winning a match
 
-- Theoretical probability of winning the tie-breaker
+## Theoretical Probabilities: Rally and Game
 
-## Slide with R Output
+$$\text{P(A Winning a Rally | A Served)} = p_A^R = \frac{\text{Points Won On Serve}}{\text{Points Served}}$$ \pause
 
+$$\text{P(A Winning a Game | A Served)}$$
+$$=p_A^G = (p_A^R)^4[1+4q_A^R+10(q_A^R)^2] +20(p_A^Rq_A^R)^3(p_A^R)^2[1-2p_A^Rq_A^R]^{-1}$$
+
+## Theoretical Probabilities: Set
+
+$$ \text{P(A Winnning a Set | A Served)} $$
+$$= p_A^S =\sum_{j=0}^4p_A^S(6,j) + p_A^S(7,5) + p_A^S(6,6)p_A^T$$ \pause
+
+Where, $p_A^S(i,j)$ is defined recursivly as:
+
+$p_A^S(0,0) = 1$, $p_A^S(i,j) = 0$ if i<0 or j<0.
+
+- if i+j -1 is even: $p_A^S(i,j) = p_A^S(i-1,j)p_A^G + p_A^S(i, j-1)q_A^G$
+
+    - omit i-1 term if j=6 and i<6
+
+    - omit j-1 term if i=6 and j<6
+
+- if i+j -1 is odd: $p_A^S(i,j) = p_A^S(i-1,j)q_B^G + p_A^S(i, j-1)p_B^G$
+
+    - omit i-1 term if j=6 and i<6
+
+    - omit j-1 term if i=6 and j<6
+
+## Theoretical Probabilities: Tie Breaker
+
+$$\text{P(A Winning the Tie Breaker | A Served Initially)} $$
+$$=p_A^T = \sum_{j=0}^5p_A^T(7,j) +  p_A^T(6,6)\sum_{n=1}^{\infty} p_A^T(n+2, n) $$ \pause
+
+Where,  $p_A^T(i,j)$ is defined recursivly as:
+
+$p_A^T(0,0) = 1$, $p_A^T(i,j) = 0$ if i<0 or j<0.
+
+- if $i+j -1 \mod 4 \equiv 0 \; \text{or} \;3$: $p_A^S(i,j) = p_A^T(i-1,j)p_A^R + p_A^T(i, j-1)q_A^R$
+
+    - omit i-1 term if j=7 and i<7
+
+    - omit j-1 term if i=7 and j<7
+
+- if $i+j -1 \mod 4 \equiv 1 \; \text{or} \; 2$: $p_A^T(i,j) = p_A^T(i-1,j)q_B^R + p_A^T(i, j-1)p_B^R$
+
+    - omit i-1 term if j=7 and i<7
+
+    - omit j-1 term if i=7 and j<7
+
+## Theoretical Probabilities: Match
+
+Women's (Best of 3):
+$$\text{P(A Winning the Match | A Served First)}$$
+$$=p_A^M = (p_A^S)^2 + 2(p_A^S)^2p_B^S$$ \pause
+
+Men's (Best of 5):
+$$\text{P(A Winning the Match | A Served First)}$$ 
+$$=p_A^M = (p_A^S)^3 + 3(p_A^S)^3p_B^S + 6(p_A^S)^3(p_B^S)^2$$
+
+## Results of Game 
 ```{r, echo = FALSE}
@@
 
-kable(TDWomen, format = "latex", booktabs = TRUE)%>%
+rownames(TDWomen) <- c("S. Williams", "V. Williams", "L. Davenport", "A. Mauresmo")
+
+kable(TDWomen, format = "latex", booktabs = TRUE, caption = "Data for the Womens Semifinalists in the 2002 U.S. Open Tournament
+")%>%
           kable_styling(latex_options = "scale_down")
@@
 
-## Slide with Plot
+```{r, echo = FALSE}
 
-```{r pressure}
-plot(pressure)
+TDMen<- as.data.frame(matrix(0, nrow = 4, ncol = 3))
+
+colnames(TDMen) <- c("P(Win a Rally)", "Empirical P(Win a Game)", "Paper P(Win a Game)" )
+
+TDMen[1, ] <- c(0.73, 0.95, 0.93)
+TDMen[2, ] <- c(0.66, 0.87, 0.85)
+TDMen[3, ] <- c(0.67, 0.85, 0.86)
+TDMen[4, ] <- c(0.68, 0.90, 0.88)
+
+OurDatWMen <- as.matrix(round(c(pg(TDMen[1,1]), pg(TDMen[2,1]), pg(TDMen[3,1]), pg(TDMen[4,1])),2))
+
+TDMen$`Our P(Win a Game)` <-(OurDatWMen)
+
+rownames(TDMen) <- c("P. Sampras", "A. Agassi", "L. Hewitt", "S. Schalken")
+
+kable(TDMen, format = "latex", booktabs = TRUE, caption = "Data for the Mens Semifinalists in the 2002 U.S. Open Tournament
+")%>%
+          kable_styling(latex_options = "scale_down")
+
 ```

### 2019-12-10 funs.R
Update2 funs

@@ -14,38 +14,41 @@ pr <- function(pwon, pserve) {
 pg <- function(pr) {
   qr <- 1 - pr
   
-  pr^4 * (1 + 4*qr + 10*qr^2) + 20*(pr*qr)^3 * pr^2 * (1 - 2*pr*qr)^-1
+  pr^4 * (1 + 4*qr + 10*qr^2) + 20 * (pr*qr)^3 * pr^2 * (1 - 2*pr*qr)^(-1)
 }
 
 
 #equation 6-8
-pASij <- function(i, j, pAG, pBG){ #i , j , prob a wins given a served, prob b wins given b served
-  if(i == 0 & j == 0){return(1)}
-  if(i < 0){return(0)}
-  if(j < 0){return(0)}
-  for( a in 1:i){ 
-    for( b in j:6){
-      if(mod((i+j-1), 2) == 1) {
-        if(j == 6 & i <= 5){
-          return(pASij(i, j-1, pAG, pBG)*(1-pAG))
-        }
-        else if( i == 6 & j <= 5){
-          return(pASij(i-1, j, pAG, pBG)*pAG)
-        }
-        else{
-          return(pASij(i-1, j, pAG, pBG)*pAG + pASij(i, j-1, pAG, pBG)*(1-pAG))
-        }
+pASij <- function(i, j, pAG, pBG) { #i , j , prob a wins given a served, prob b wins given b served
+  # initial conditions
+  if(i == 0 & j == 0) return(1)
+  if(i < 0) return(0)
+  if(j < 0) return(0)
+  
+  
+  for( a in i:0) {
+    
+    for( b in j:6) {
+      
+      # even i-1 + j
+      if(mod((a-1+b), 2) == 0) {
+        
+        if(a == 6 & b <= 5) return( pASij(a, b-1, pAG, pBG)*(1-pAG) )
+        
+        else if( a == 6 & b <= 5) return( pASij(a-1, b, pAG, pBG)*pAG )
+    
+        return( pASij(a-1, b, pAG, pBG)*pAG + pASij(a, b-1, pAG, pBG)*(1-pAG))
+        
       }
-      else{
-        if(j == 6 & i <= 5){
-          return(pASij(i, j-1, pAG, pBG)*pBG)
-        }
-        else if( i == 6 & j <= 5){
-          return(pASij(i-1, j, pAG, pBG)*(1-pBG))
[…]

### 2019-12-10 funs.R
Update

@@ -111,11 +111,7 @@ pM <- function(ps_a, ps_b, num_set){
     ret <- (ps_a)^2 + 2*(ps_a)^2 * ps_b
   }
   if(num_set==3){
-<<<<<<< HEAD
     ret <- (ps_a)^3 + 3*(ps_a)^3 * ps_b + 6*ps_a^3 * (ps_b)^2
-=======
-    ret <- (ps_a)^3+3*(ps_a)^3*(1-ps_b)+6*ps_a^3*(1-ps_b)^2
->>>>>>> 5546f7c00b32d3cbe619a7ab20e6aaab4278c373
   }
   
   if(ret>1) return(1)
@@ -162,8 +158,6 @@ pTC <- function(pr_1, pr_2, pr_3, pr_4, numset) {
   p42 <- 1 - p24
   p43 <- 1 - p34
   
-<<<<<<< HEAD
-  
   p14 <- 1 - p41
   p13 <- 1 - p31
   p12 <- 1 - p21
@@ -174,12 +168,6 @@ pTC <- function(pr_1, pr_2, pr_3, pr_4, numset) {
              p34 * (p31*p12 + p32*p21),
              p43 * (p41*p12 + p42*p21)))
 }
-=======
-  c(p12 * (p13*p34 + p14*p43),
-    p21 * (p23*p34 + p24*p43),
-    p34 * (p31*p12 + p32*p21),
-    p43 * (p41*p12 + p42*p21))
-}
 
 
 
@@ -197,4 +185,3 @@ pTC <- function(pr_1, pr_2, pr_3, pr_4, numset) {
 
 
 
->>>>>>> 5546f7c00b32d3cbe619a7ab20e6aaab4278c373

### 2019-12-10 funs.R
Update: needs cleaning

@@ -26,32 +26,32 @@ pASij <- function(i, j, pAG, pBG) { #i , j , prob a wins given a served, prob b 
   if(j < 0) return(0)
   
   
-  for( a in i:0) {
-    
-    for( b in j:6) {
+  # for( i in i:0) {
+  #   
+  #   for( j in j:6) {
       
       # even i-1 + j
-      if(mod((a-1+b), 2) == 0) {
+      if(mod((i-1+j), 2) == 0) {
         
-        if(a == 6 & b <= 5) return( pASij(a, b-1, pAG, pBG)*(1-pAG) )
+        if(j == 6 & i <= 5) return( pASij(i, j-1, pAG, pBG)*(1-pAG) )
         
-        else if( a == 6 & b <= 5) return( pASij(a-1, b, pAG, pBG)*pAG )
+        else if( i == 6 & j <= 5) return( pASij(i-1, j, pAG, pBG)*pAG )
     
-        return( pASij(a-1, b, pAG, pBG)*pAG + pASij(a, b-1, pAG, pBG)*(1-pAG))
+        return( pASij(i-1, j, pAG, pBG)*pAG + pASij(i, j-1, pAG, pBG)*(1-pAG))
         
       }
       # odd i-1 + j
       else {
         
-        if(b == 6 & a <= 5) return( pASij(a, b-1, pAG, pBG)*pBG )
+        if(j == 6 & i <= 5) return( pASij(i, j-1, pAG, pBG)*pBG )
         
-        else if( a == 6 & b <= 5) return( pASij(a-1, b, pAG, pBG)*(1-pBG) )
+        else if( i == 6 & j <= 5) return( pASij(i-1, j, pAG, pBG)*(1-pBG) )
         
-        return( pASij(a-1, b, pAG, pBG)*(1-pBG) + pASij(a, b-1, pAG, pBG)*pBG )
+        return( pASij(i-1, j, pAG, pBG)*(1-pBG) + pASij(i, j-1, pAG, pBG)*pBG )
         
       }
-    }
-  }
+  #   }
+  # }
   
 }
 
@@ -64,31 +64,31 @@ pATij <- function(i, j, pAR, pBR) { #i , j , prob a wins given a served, prob b 
   if(j < 0) return(0)
   
   
-  for( a in i:0) { 
-    
-    for( b in j:7) {
+  # for( i in i:0) { 
+  #   
+  #   for( j in j:7) {
[…]

### 2019-12-10 funs.R
Still need to fix pTC; Cleaned other code

@@ -26,33 +26,23 @@ pASij <- function(i, j, pAG, pBG) { #i , j , prob a wins given a served, prob b 
   if(j < 0) return(0)
   
   
-  # for( i in i:0) {
-  #   
-  #   for( j in j:6) {
-      
-      # even i-1 + j
-      if(mod((i-1+j), 2) == 0) {
+  if(mod((i-1+j), 2) == 0) {
         
-        if(j == 6 & i <= 5) return( pASij(i, j-1, pAG, pBG)*(1-pAG) )
+    if(j == 6 & i <= 5) return( pASij(i, j-1, pAG, pBG)*(1-pAG) )
         
-        else if( i == 6 & j <= 5) return( pASij(i-1, j, pAG, pBG)*pAG )
+    else if( i == 6 & j <= 5) return( pASij(i-1, j, pAG, pBG)*pAG )
     
-        return( pASij(i-1, j, pAG, pBG)*pAG + pASij(i, j-1, pAG, pBG)*(1-pAG))
+    return( pASij(i-1, j, pAG, pBG)*pAG + pASij(i, j-1, pAG, pBG)*(1-pAG))
         
-      }
-      # odd i-1 + j
-      else {
+  } else {
         
-        if(j == 6 & i <= 5) return( pASij(i, j-1, pAG, pBG)*pBG )
+    if(j == 6 & i <= 5) return( pASij(i, j-1, pAG, pBG)*pBG )
         
-        else if( i == 6 & j <= 5) return( pASij(i-1, j, pAG, pBG)*(1-pBG) )
+    else if( i == 6 & j <= 5) return( pASij(i-1, j, pAG, pBG)*(1-pBG) )
         
-        return( pASij(i-1, j, pAG, pBG)*(1-pBG) + pASij(i, j-1, pAG, pBG)*pBG )
+    return( pASij(i-1, j, pAG, pBG)*(1-pBG) + pASij(i, j-1, pAG, pBG)*pBG )
         
-      }
-  #   }
-  # }
-  
+  }
 }
 
 
@@ -62,34 +52,26 @@ pATij <- function(i, j, pAR, pBR) { #i , j , prob a wins given a served, prob b 
   if(i == 0 & j == 0) return(1)
   if(i < 0) return(0)
   if(j < 0) return(0)
-  
-  
-  # for( i in i:0) { 
-  #   
-  #   for( j in j:7) {
       
-      MO <- mod(i+j-1, 4)
[…]

### 2019-12-10 Group1Prez.Rmd
That's not my name!

@@
 title: "Group 1: Tennis "
-author: "Olivia Beck, Emma Wilson, Ryan Volkert"
+author: "Olivia Beck, Emma Lewis, Ryan Volkert"
 date: "December 12, 2019"

### 2019-12-10 Group1Prez.Rmd
Added to slides. Added more explaination on variables and flowchart about points.

@@
 
+## Project
+
+- Project based off a paper by Paul K. Newton and Joseph B. Keller called Probability of Winning at Tennis 1. Theory and Data
+
+- Paper discussed calculating the probability that one player, A, wins a tennis match against another player, B
+
+- Based on other papers involving calculating the probability of winning a game in other racket sports the conclusion was made to treat points in tennis as  independent identically distributed (iid) random variables
+
+- Although it is noted at points in tennis are not iid for most purposes this is not a bad assumption as the divergence from iid is small
+
+  - This was supported by a statistical anaylsis of 4 years of Wimbledon data
+
 ## The Game of Tennis
@@
 - Tie-break game: If a game score of 6-6 is reached and tie-break set rules are used. In a tie-break game, a player/team must reach 7 points with a two point advantage to win
+
+## Game of Tennis 
+![](tennis-scoring.jpg){ width=85% }\
 
@@
 $$=p_A^G = (p_A^R)^4[1+4q_A^R+10(q_A^R)^2] +20(p_A^Rq_A^R)^3(p_A^R)^2[1-2p_A^Rq_A^R]^{-1}$$
+
+- Where Probability A loses a rally given A served:$$q_A^R = 1-\frac{\text{Points Won On Serve}}{\text{Points Served}}$$
 
@@
 
+Where:
+
+- $$p_A^S=\text{Probabilty A wins a set given A served}$$
+
+- $$p_B^S=\text{Probabilty B wins a set given B served}$$
+
 ## Results of Game 

### 2019-12-11 funs.R
complete pTC; needs to debug other funs

@@ -80,15 +80,15 @@ pT <- function(pAR, pBR) {
     (1 - pAR*pBR - (1-pAR)*(1-pBR))^-1
 }
 
-#Prob A wins a set given a served 
-ps <- function(pAR, pBR){
+# Prob A wins a set given a served
+ps <- function(pAR, pBR) {
   pag <- pg(pAR)
   pbg <- pg(pBR)
   
   ret <- pASij(7,5, pag, pbg) + pASij(6,6,pAR,pBR)*pT(pAR, pBR) + sum(sapply(0:4, pASij, i=6, pAG=pag, pBG=pbg ))
   
-  if(ret > 1){return(1)}
-  else {return(ret)}
+  if(ret > 1) return(1)
+  return(ret)
 }
 
 
@@ -98,47 +98,41 @@ ps <- function(pAR, pBR){
 #pbg is prob B wins a game given B served
 
 ## The probability of winning two out of three sets, resulting in winning a match
-pM <- function(pAR, pBR, num_set){
+pM <- function(pAR, pBR, num_set) {
   ps_a <- ps(pAR, pBR)
   ps_b <- ps(pBR, pAR)
   
-  if (num_set==2){
-    ret <- (ps_a)^2 + 2*(ps_a)^2 * ps_b
-  }
-  if(num_set==3){
-    ret <- (ps_a)^3 + 3*(ps_a)^3 * ps_b + 6*ps_a^3 * (ps_b)^2
-  }
+  if (num_set==2) ret <- (ps_a)^2 + 2*(ps_a)^2 * ps_b
+  
+  else if(num_set==3) ret <- (ps_a)^3 + 3*(ps_a)^3 * ps_b + 6*ps_a^3 * (ps_b)^2
   
   return(ret)
 }
 
 # Probability of winning a tournament
-pTC <- function(pr_1, pr_2, pr_3, pr_4, numset) {
-  pRally <- c(pr_1, pr_2, pr_3, pr_4)
+pTC <- function(pr1, pr2, pr3, pr4, numset) {
+  p0 <- cbind(rep(1,4))
   
+  P1 <- rbind(c(0, pM(pr1, pr2, numset), 0, 0),
+              c(pM(pr2, pr1, numset), 0, 0, 0),
+              c(0, 0, 0, pM(pr3, pr4, numset)),
[…]

### 2019-12-11 Group1Prez.Rmd
Updated slides and added a slide about info on data used

@@
 
-- Where Probability A loses a rally given A served:$$q_A^R = 1-\frac{\text{Points Won On Serve}}{\text{Points Served}}$$
+- Where Probability A loses a rally given A served: 
+$$q_A^R = 1-\frac{\text{Points Won On Serve}}{\text{Points Served}}$$
 
@@
 
-- $$p_A^S=\text{Probabilty A wins a set given A served}$$
+- $p_A^S=\text{Probabilty A wins a set given A served}$
 
-- $$p_B^S=\text{Probabilty B wins a set given B served}$$
+- $p_B^S=\text{Probabilty B wins a set given B served}$
+
+## Data being used 
+Data used in paper:
+
+  - Men and Women semifinalists in the 2002 U.S Open tournament
+
+  - Men and Women semifinalists in the 2002 Wimbledon tournament
+
+Data used in our simulation:
+
+  - Men and Women semifinalists in the 2019 Wibledon tournament
 

### 2019-12-11 funs.R
Update again

@@ -19,96 +19,75 @@ pg <- function(pr) {
 
 
 #equation 6-8
-pASij <- function(i, j, pAG, pBG){ #i , j , prob a wins given a served, prob b wins given b served
-  if(i == 0 & j == 0){return(1)}
-  if(i < 0){return(0)}
-  if(j < 0){return(0)}
-  for( a in 1:i){ 
-    for( b in j:6){
-      if(mod((i+j-1), 2) == 1) {
-        if(j == 6 & i <= 5){
-          return(pASij(i, j-1, pAG, pBG)*(1-pAG))
-        }
-        else if( i == 6 & j <= 5){
-          return(pASij(i-1, j, pAG, pBG)*pAG)
-        }
-        else{
-          return(pASij(i-1, j, pAG, pBG)*pAG + pASij(i, j-1, pAG, pBG)*(1-pAG))
-        }
-      }
-      else{
-        if(j == 6 & i <= 5){
-          return(pASij(i, j-1, pAG, pBG)*pBG)
-        }
-        else if( i == 6 & j <= 5){
-          return(pASij(i-1, j, pAG, pBG)*(1-pBG))
-        }
-        else{
-          return(pASij(i-1, j, pAG, pBG)*(1-pBG) + pASij(i, j-1, pAG, pBG)*pBG)
-        }
-      }
-    }
-  }
+pASij <- function(i, j, pAG, pBG) { #i , j , prob a wins given a served, prob b wins given b served
+  # initial conditions
+  if(i == 0 & j == 0) return(1)
+  if(i < 0) return(0)
+  if(j < 0) return(0)
   
+  
+  if(mod((i-1+j), 2) == 0) {
+    
+    if(j == 6 & i <= 5) return( pASij(i, j-1, pAG, pBG)*(1-pAG) )
+    
+    else if( i == 6 & j <= 5) return( pASij(i-1, j, pAG, pBG)*pAG )
+    
+    return( pASij(i-1, j, pAG, pBG)*pAG + pASij(i, j-1, pAG, pBG)*(1-pAG))
+    
+  } else {
+    
+    if(j == 6 & i <= 5) return( pASij(i, j-1, pAG, pBG)*pBG )
+    
[…]

### 2019-12-11 Group1Prez.Rmd

@@
 
-- Paper discussed calculating the probability that one player, A, wins a tennis match against another player, B
+- Paper discussed how the probability of winning a game, a set, and a match in tennis are computed based on each player's probability of winning a point on a serve
 
-- Based on other papers involving calculating the probability of winning a game in other racket sports the conclusion was made to treat points in tennis as  independent identically distributed (iid) random variables
+- Based on other papers the conclusion was made to treat serves in tennis as independent identically distributed (iid) random variables
 
-- Although it is noted at points in tennis are not iid for most purposes this is not a bad assumption as the divergence from iid is small
+- It is noted that points in tennis are not iid for most purposes this is not a bad assumption as the divergence from iid is small
 
-  - This was supported by a statistical anaylsis of 4 years of Wimbledon data
+- Both two out of three and three out of five set matches were considered aloowing for 13-point tiebreaker in each set if needed
 

### 2019-12-11 PaperDraft.Rmd
Outline
echo = FALSE

@@
 ```{r setup, include=FALSE}
-knitr::opts_chunk$set(echo = TRUE)
+knitr::opts_chunk$set(echo = FALSE)
 ```
@@
 ### Motivation 
+The probability of winning a game, a set, and a match in tennis are calculated based on the each's players probability of winning a point on a serve.
+This paper and the reference paper, The Probability of Winning at Tennis 1.
+Theory and Data written by Paul K.
+Newton and Joseph B.
+keller both make the assumption that each serve is an independently and identically distributed (iid) random variable.
+This assumption has been made in other reports relating to the probability of winning a game in other racuet sports and even though serves in tennis are not actually iid random varibales for most purposes this is not a bad assumption as the divergence from iid is small.
+- Explination of Game, Set, Match
 
-- Explination of Game, Set, Match
+- How likely are the players to win the torunament?
 
@@
 
+- Reproduce data in paper
+
 ### Extension
+
+- Same thing with new tournament
+
+- Maybe with new method if we have time
+
+### Bibliography

### 2019-12-11 PaperDraft.Rmd
Bad update

@@
 This assumption has been made in other reports relating to the probability of winning a game in other racuet sports and even though serves in tennis are not actually iid random varibales for most purposes this is not a bad assumption as the divergence from iid is small.
+
+A game in tennis is played with one player serving and is one by the first player to score four or more points and to be at least two points ahead of the other player.
+Player A can win a game against player B by a score of (4,0), (4,1) or (4,2), or else the score becomes (3,3) which is called "deuce".
 - Explination of Game, Set, Match

### 2019-12-11 funs.R

@@ -91,8 +91,6 @@ pATij <- function(i, j, pAR, pBR){ #i , j , prob a wins given a served, prob b w
 
 
 
-
-<<<<<<< HEAD
 # Prob A wins a set given a served
 ps <- function(pAR, pBR) {
   pag <- pg(pAR)
@@ -102,13 +100,6 @@ ps <- function(pAR, pBR) {
   
   if(ret > 1) return(1)
   return(ret)
-=======
-#Prob A wins a set given a served 
-ps <- function(pag, pbg){
-  ret <- pASij(7,5, pag, pbg) + pATij(6,6,pag, pbg) + sum(sapply(0:4, pASij, i=6, pAG=pag, pBG=pbg ))
-  if(ret > 1){return(1)}
-  else {return(ret)}
->>>>>>> 965c6ad4784ebd958646c760a2a7228f6a02ad5b
 }
 
 
@@ -151,9 +142,9 @@ pTC <- function(pr1, pr2, pr3, pr4, numset) {
   t(p1 * p2)
 }
 
-100 * (pg1)^3 * qg1^2 * pg2^2 * qg2^3 +
-  40 * pg1^2 * qg1^3 * pg2 * qg2^4 +
-  20 * pg1^4 * qg1 * pg2^3 * qg2^2 +
-  5 * pg1 * qg1^4 * qg2^5 +
-  pg1^5 * pg2^4 * qg2
+#100 * (pg1)^3 * qg1^2 * pg2^2 * qg2^3 +
+ # 40 * pg1^2 * qg1^3 * pg2 * qg2^4 +
+  #20 * pg1^4 * qg1 * pg2^3 * qg2^2 +
+  #5 * pg1 * qg1^4 * qg2^5 +
+  #pg1^5 * pg2^4 * qg2
 

### 2019-12-11 PaperDraft.Rmd
Updated scoring picture

--- 2019-11-11 PaperDraft.Rmd
@@
 
-- Explination of Game, Set, Match
+- How likely are the players to win the tournament?
+
+The probability of winning a game, a set, and a match in tennis are calculated based on the each players probability of winning a point on a serve.
+This paper and the reference paper, The Probability of Winning at Tennis 1.
+Theory and Data written by Paul K.
+Newton and Joseph B.
+Keller both make the assumption that each serve is an independently and identically distributed (iid) random variable.
+This assumption has been made in other reports relating to the probability of winning a game in other racket sports and even though serves in tennis are not actually iid random variables for most purposes this is not a bad assumption as the divergence from iid is small.
+
+A game in tennis is played with one player serving and is won by the first player to score four or more points and to be at least two points ahead of the other player.
+Player A can win a game against player B by a score of (4,0), (4,1) or (4,2), or else the score becomes (3,3) which is called "deuce".
+
+In a set the players alternate serving until a player wins at least six games and is ahead by at least two games.
+If the game score reaches 6-6, a 13-point tiebreaker is used to determine who wins the set.
+
+To win a match a player in woman's format a player must win two out of three sets and in men's format a player must win three out of five sets.
 

### 2019-12-11 Group1Prez.Rmd
just ignore these
Merge branch 'master' of https://github.com/stat400-csu/project_1

# Conflicts:
#	Group1Prez.Rmd
#	Group1Prez.aux
#	Group1Prez.nav
#	Group1Prez.pdf
#	Group1Prez.snm
#	funs.R

@@
 ```{r setup, include=FALSE, warning=FALSE}
-knitr::opts_chunk$set(echo = FALSE)
 source("funs.R")

### 2019-12-11 Group1Prez.Rmd
Done up until new data

@@
 ```
-
+\pause
 ```{r, echo = FALSE}
@@
 ```
+
+## Tournament Results: Women
+```{r, echo=FALSE}
+Tourney1_Women = data.frame(`P(Winning a Rally)` = TDWomen[,1],
+                            `Paper P(Winning the Tournement)` = c(.2872, .3599, .0482, .3074))
+#`Our P(Winning the Tournement )` =round( pTC(TDWomen[1,1],TDWomen[2,1],TDWomen[3,1],TDWomen[4,1], 2), 4)
+
+rownames(Tourney1_Women)<- c("S. Williams","L. Davenport",  "A. Mauresmo", "V. Williams")
+
+T1<- table(base::sample(rownames(Tourney1_Women), 2000, prob = Tourney1_Women$Paper.P.Winning.the.Tournement., replace = TRUE))
+
+Winner1 <- which(T1 == max(T1))
+#Winner1
+
+#T2<- table(base::sample(rownames(Tourney1_Women), 2000, prob = Tourney1_Women$Our.P.Winning.the.Tournement., replace = TRUE)) 
+#Winner2 <- which(T2 == max(T2))
+#Winner2
+
+ggplot(data.frame(T1)) +
+  geom_col(aes(x=Var1, y=Freq)) +
+  xlab("Players") +
+  ggtitle("Which Player Won the Tournement?")
+
+```
+
+## Tournament Results: Men
+```{r, echo=FALSE}
+Tourney1_Men = data.frame(`P(Winning a Rally)` = TDMen[,1],
+                            `Paper P(Winning the Tournement)` = c(.2872, .3599, .0482, .3074))
+#`Our P(Winning the Tournement )` =round( pTC(TDMen[1,1],TDMen[2,1],TDMen[3,1],TDMen[4,1], 2), 4)
+
+rownames(Tourney1_Men)<- c("P. Sampras","S. Schalken",  "A. Agassi", "L. Hewitt")
+
+T1<- table(base::sample(rownames(Tourney1_Men), 2000, prob = Tourney1_Men$Paper.P.Winning.the.Tournement., replace = TRUE))
+
+Winner1 <- which(T1 == max(T1))
+#Winner1
+
+#T2<- table(base::sample(rownames(Tourney1_Men), 2000, prob = Tourney1_Men$Our.P.Winning.the.Tournement., replace = TRUE)) 
+#Winner2 <- which(T2 == max(T2))
+#Winner2
+
+ggplot(data.frame(T1)) +
+  geom_col(aes(x=Var1, y=Freq)) +
+  xlab("Players") +
+  ggtitle("Which Player Won the Tournement?")
+
+```

### 2019-12-11 funs.R
comments

@@ -141,25 +141,25 @@ pTC <- function(pr1, pr2, pr3, pr4, numset) {
   p1 * p2
 }
 
-60 * (pg1)^3 * qg1^2 * pg2^2 * qg2^3 +
-  40 * pg1^2 * qg1^3 * pg2 * qg2^4 +
-  20 * pg1^4 * qg1 * pg2^3 * qg2^2 +
-  5 * pg1 * qg1^4 * qg2^5 +
-  pg1^5 * pg2^4 * qg2
-
-30 * pr1^2 * (1-pr1)^4 * pr2 * (1-pr2)^5 +
-  pr1 * (1-pr1)^5 * (1-pr2)^6 +
-  200 * pr1^4 * (1-pr1)^2 * pr2^3 * (1-pr2)^3 +
-  75 * pr1^5 * (1-pr1) * pr2^4 * (1-pr2)^2 +
-  150 * pr1^3 * (1-pr1)^3 * pr2^2 * (1-pr2)^4 +
-  6 * pr1^6 * pr2^5 * (1-pr2)
-
-s=0
-for(i in 0:4) {
-  s <- s + pASij(i, 6, pag, pbg) + pASij(6,i, pag, pbg)
-}
-
-1 -
-  (s +
-     pASij(7,5, pag, pbg) +
-     pASij(5,7, pag, pbg))
+# 60 * (pg1)^3 * qg1^2 * pg2^2 * qg2^3 +
+#   40 * pg1^2 * qg1^3 * pg2 * qg2^4 +
+#   20 * pg1^4 * qg1 * pg2^3 * qg2^2 +
+#   5 * pg1 * qg1^4 * qg2^5 +
+#   pg1^5 * pg2^4 * qg2
+# 
+# 30 * pr1^2 * (1-pr1)^4 * pr2 * (1-pr2)^5 +
+#   pr1 * (1-pr1)^5 * (1-pr2)^6 +
+#   200 * pr1^4 * (1-pr1)^2 * pr2^3 * (1-pr2)^3 +
+#   75 * pr1^5 * (1-pr1) * pr2^4 * (1-pr2)^2 +
+#   150 * pr1^3 * (1-pr1)^3 * pr2^2 * (1-pr2)^4 +
+#   6 * pr1^6 * pr2^5 * (1-pr2)
+# 
+# s=0
+# for(i in 0:4) {
+#   s <- s + pASij(i, 6, pag, pbg) + pASij(6,i, pag, pbg)
[…]

### 2019-12-11 Probability of winning a set broken down .R
Created Probability of winning a set broken down

@@ -1,0 +1,32 @@
+pga= 0.5
+qga= 1-pga
+
+pgb=0.5
+qga=1-pgb
+
+A1=(pga*qga)^3
+
+A2=3*(pga)^3*(qga)*(qbg)^3
+  +3*(pga)^4*(pgb)*(qgb)^2
+
+A3=12*(pga)^3*(qga)*(pgb)*(qgb)^3
+  +6*(pga)^2*(qga)^2*(qgb)^4
+  +3*(pga)^4*(pgb)^2*(qgb)^2
+
+A4=24*(pga)^3*(qga)^2*(pgb)*qgb^3
+  +24*(pga)^4*(qga)*(pgb)^2*(qgb)^2
+  +4*(pga)^2*(qga)^3*(qga)^4
+  +4*(pga)^5*(pgb)^3*(qgb)
+
+A5=60*(pga)^3*(qga)^2*(pgb)^2*(qgb)^3
+  +40*(pga)^2*(qga)^3*(pgb)*(qga)^4
+  +20*(pga)^4*(qga)*(pgb)^3*(qgb)^2
+  +5*(pga)*(qga)^4*(qgb)^5
+  +(pga)^5*(pga)^4*(qgb)
+
+A6=100*(pga)^3*(qga)^3*(pgb)^2*(qgb)^4
++100*(pga)^4*(qga)^2*(pgb)^3*(qgb)^3
++25*(pga)^2*(qga)^4*(pgb)*(qgb)^5
++25*(pga)^5*(qga)*(pgb)^4*(qgb)^2
++pga*(qga)^5*(qgb)^6
++(pga)^6*(pgb)^5*qgb

### 2019-12-11 Group1Prez.Rmd
Fixed mens data

@@
 Tourney1_Men = data.frame(`P(Winning a Rally)` = TDMen[,1],
-                            `Paper P(Winning the Tournement)` = c(.2872, .3599, .0482, .3074))
+                            `Paper P(Winning the Tournement)` = c(.6747, .0851, .0945, .1457))
 #`Our P(Winning the Tournement )` =round( pTC(TDMen[1,1],TDMen[2,1],TDMen[3,1],TDMen[4,1], 2), 4)

### 2019-12-11 Probability of winning a set broken down .R
It still broke

@@ -1,32 +1,73 @@
-pga= 0.5
-qga= 1-pga
+A1 <- function(pga, pgb) {
+  qgb <- 1 - pgb
+  qga <- 1 - pga
+  
+  (pga*qgb)^3
+}
 
-pgb=0.5
-qga=1-pgb
+A2 <- function(pga, pgb) {
+  qgb <- 1 - pgb
+  qga <- 1 - pga
+  
+  3*(pga)^3*(qga)*(qgb)^3
+    +3*(pga)^4*(pgb)*(qgb)^2
+}
 
-A1=(pga*qga)^3
+A3 <- function(pga, pgb) {
+  qgb <- 1 - pgb
+  qga <- 1 - pga
+  
+  12*(pga)^3*(qga)*(pgb)*(qgb)^3
+    +6*(pga)^2*(qga)^2*(qgb)^4
+    +3*(pga)^4*(pgb)^2*(qgb)^2
+}
 
-A2=3*(pga)^3*(qga)*(qbg)^3
-  +3*(pga)^4*(pgb)*(qgb)^2
+A4 <- function(pga, pgb) {
+  qgb <- 1 - pgb
+  qga <- 1 - pga
+  
+  24*(pga)^3*(qga)^2*(pgb)*qgb^3
+    +24*(pga)^4*(qga)*(pgb)^2*(qgb)^2
+    +4*(pga)^2*(qga)^3*(qgb)^4
+    +4*(pga)^5*(pgb)^3*(qgb)
+}
 
-A3=12*(pga)^3*(qga)*(pgb)*(qgb)^3
-  +6*(pga)^2*(qga)^2*(qgb)^4
-  +3*(pga)^4*(pgb)^2*(qgb)^2
+A5 <- function(pga, pgb) {
+  qgb <- 1 - pgb
+  qga <- 1 - pga
+  
+  60*(pga)^3*(qga)^2*(pgb)^2*(qgb)^3
+    +40*(pga)^2*(qga)^3*(pgb)*(qga)^4
+    +20*(pga)^4*(qga)*(pgb)^3*(qgb)^2
+    +5*(pga)*(qga)^4*(qgb)^5
+    +(pga)^5*(pgb)^4*(qgb)
+}
 
-A4=24*(pga)^3*(qga)^2*(pgb)*qgb^3
-  +24*(pga)^4*(qga)*(pgb)^2*(qgb)^2
-  +4*(pga)^2*(qga)^3*(qga)^4
[…]

### 2019-12-11 Group1Prez.Rmd
Updated

--- 2019-12-11 Group1Prez.Rmd
@@
 ```{r setup, include=FALSE, warning=FALSE}
+knitr::opts_chunk$set(echo = FALSE)
 source("funs.R")
@@
 ## Game of Tennis 
-![](tennis-scoring.jpg){ width=85% }\
+![](Scoring.jpg){ width=85% }\
 

### 2019-12-11 Probability of winning a set broken down .R

@@ -2,27 +2,27 @@ pga= 0.5
 qga= 1-pga
 
 pgb=0.5
-qga=1-pgb
+qgb=1-pgb
 
-A1=(pga*qga)^3
+A1=(pga*qgb)^3
 
-A2=3*(pga)^3*(qga)*(qbg)^3
+A2=3*(pga)^3*(qga)*(qgb)^3
   +3*(pga)^4*(pgb)*(qgb)^2
 
 A3=12*(pga)^3*(qga)*(pgb)*(qgb)^3
   +6*(pga)^2*(qga)^2*(qgb)^4
   +3*(pga)^4*(pgb)^2*(qgb)^2
 
-A4=24*(pga)^3*(qga)^2*(pgb)*qgb^3
+A4=24*(pga)^3*(qga)^2*(pgb)*(qgb)^3
   +24*(pga)^4*(qga)*(pgb)^2*(qgb)^2
-  +4*(pga)^2*(qga)^3*(qga)^4
+  +4*(pga)^2*(qga)^3*(qgb)^4
   +4*(pga)^5*(pgb)^3*(qgb)
 
 A5=60*(pga)^3*(qga)^2*(pgb)^2*(qgb)^3
   +40*(pga)^2*(qga)^3*(pgb)*(qga)^4
   +20*(pga)^4*(qga)*(pgb)^3*(qgb)^2
   +5*(pga)*(qga)^4*(qgb)^5
-  +(pga)^5*(pga)^4*(qgb)
+  +(pga)^5*(pgb)^4*(qgb)
 
 A6=100*(pga)^3*(qga)^3*(pgb)^2*(qgb)^4
 +100*(pga)^4*(qga)^2*(pgb)^3*(qgb)^3

### 2019-12-11 funs.R
Deleted bad function

@@ -141,25 +141,3 @@ pTC <- function(pr1, pr2, pr3, pr4, numset) {
   p1 * p2
 }
 
-60 * (pg1)^3 * qg1^2 * pg2^2 * qg2^3 +
-  40 * pg1^2 * qg1^3 * pg2 * qg2^4 +
-  20 * pg1^4 * qg1 * pg2^3 * qg2^2 +
-  5 * pg1 * qg1^4 * qg2^5 +
-  pg1^5 * pg2^4 * qg2
-
-30 * pr1^2 * (1-pr1)^4 * pr2 * (1-pr2)^5 +
-  pr1 * (1-pr1)^5 * (1-pr2)^6 +
-  200 * pr1^4 * (1-pr1)^2 * pr2^3 * (1-pr2)^3 +
-  75 * pr1^5 * (1-pr1) * pr2^4 * (1-pr2)^2 +
-  150 * pr1^3 * (1-pr1)^3 * pr2^2 * (1-pr2)^4 +
-  6 * pr1^6 * pr2^5 * (1-pr2)
-
-s=0
-for(i in 0:4) {
-  s <- s + pASij(i, 6, pag, pbg) + pASij(6,i, pag, pbg)
-}
-
-1 -
-  (s +
-     pASij(7,5, pag, pbg) +
-     pASij(5,7, pag, pbg))

### 2019-12-11 funs.R
add ps(7,5)

@@ -25,18 +25,26 @@ pASij <- function(i, j, pAG, pBG) { #i , j , prob a wins given a served, prob b 
   if(i < 0) return(0)
   if(j < 0) return(0)
   
-  if(i == 6 & j == 6) {
-    s <- 0
-    
-    for(x in 0:4) {
-      s <- s + pASij(x, 6, pag, pbg) + pASij(6, x, pag, pbg)
-    }
-    
-    return(1 -
-      (s +
-         pASij(7,5, pag, pbg) +
-         pASij(5,7, pag, pbg)))
+  
+  
+  if( i == 7 & j==5){
+    return(pASij(6,5, pAG, pBG) *(1-pBG))
   }
+  
+  
+  
+  # if(i == 6 & j == 6) {
+  #   s <- 0
+  #   
+  #   for(x in 0:4) {
+  #     s <- s + pASij(x, 6, pag, pbg) + pASij(6, x, pag, pbg)
+  #   }
+  #   
+  #   return(1 -
+  #     (s +
+  #        pASij(7,5, pag, pbg) +
+  #        pASij(5,7, pag, pbg)))
+  # }
   
   if(mod((i-1+j), 2) == 0) {
     

### 2019-12-11 funs_new.R
Cleaning it up

@@ -110,8 +110,6 @@ ps <- function(pAR, pBR) {
     pASij(6,6, pag, pbg) * pT(pAR, pBR)
 }
 
-source('Probability of winning a set broken down .R')
-
 
 #where pag is prob A wins a game given A served and 
 #pbg is prob B wins a game given B served
@@ -148,27 +146,4 @@ pTC <- function(pr1, pr2, pr3, pr4, numset) {
   
   p1 * p2
 }
-
-# 60 * (pg1)^3 * qg1^2 * pg2^2 * qg2^3 +
-#   40 * pg1^2 * qg1^3 * pg2 * qg2^4 +
-#   20 * pg1^4 * qg1 * pg2^3 * qg2^2 +
-#   5 * pg1 * qg1^4 * qg2^5 +
-#   pg1^5 * pg2^4 * qg2
-# 
-# 30 * pr1^2 * (1-pr1)^4 * pr2 * (1-pr2)^5 +
-#   pr1 * (1-pr1)^5 * (1-pr2)^6 +
-#   200 * pr1^4 * (1-pr1)^2 * pr2^3 * (1-pr2)^3 +
-#   75 * pr1^5 * (1-pr1) * pr2^4 * (1-pr2)^2 +
-#   150 * pr1^3 * (1-pr1)^3 * pr2^2 * (1-pr2)^4 +
-#   6 * pr1^6 * pr2^5 * (1-pr2)
-# 
-# s=0
-# for(i in 0:4) {
-#   s <- s + pASij(i, 6, pag, pbg) + pASij(6,i, pag, pbg)
-# }
-# 
-# 1 -
-#   (s +
-#      pASij(7,5, pag, pbg) +
-#      pASij(5,7, pag, pbg))
 

### 2019-12-11 Probability of winning a set broken down .R
Do not need anymore

@@ -1,73 +1,0 @@
-A1 <- function(pga, pgb) {
-  qgb <- 1 - pgb
-  qga <- 1 - pga
-  
-  (pga*qgb)^3
-}
-
-A2 <- function(pga, pgb) {
-  qgb <- 1 - pgb
-  qga <- 1 - pga
-  
-  3*(pga)^3*(qga)*(qgb)^3
-  +3*(pga)^4*(pgb)*(qgb)^2
-}
-
-A3 <- function(pga, pgb) {
-  qgb <- 1 - pgb
-  qga <- 1 - pga
-  
-  12*(pga)^3*(qga)*(pgb)*(qgb)^3
-  +6*(pga)^2*(qga)^2*(qgb)^4
-  +3*(pga)^4*(pgb)^2*(qgb)^2
-}
-
-A4 <- function(pga, pgb) {
-  qgb <- 1 - pgb
-  qga <- 1 - pga
-  
-  24*(pga)^3*(qga)^2*(pgb)*qgb^3
-  +24*(pga)^4*(qga)*(pgb)^2*(qgb)^2
-  +4*(pga)^2*(qga)^3*(qgb)^4
-  +4*(pga)^5*(pgb)^3*(qgb)
-}
-
-A5 <- function(pga, pgb) {
-  qgb <- 1 - pgb
-  qga <- 1 - pga
-  
-  60*(pga)^3*(qga)^2*(pgb)^2*(qgb)^3
-  +40*(pga)^2*(qga)^3*(pgb)*(qga)^4
-  +20*(pga)^4*(qga)*(pgb)^3*(qgb)^2
-  +5*(pga)*(qga)^4*(qgb)^5
-  +(pga)^5*(pgb)^4*(qgb)
-}
-
-A6 <- function(pga, pgb) {
-  qgb <- 1 - pgb
-  qga <- 1 - pga
-  
-  100*(pga)^3*(qga)^3*(pgb)^2*(qgb)^4
-  +100*(pga)^4*(qga)^2*(pgb)^3*(qgb)^3
-  +25*(pga)^2*(qga)^4*(pgb)*(qgb)^5
-  +25*(pga)^5*(qga)*(pgb)^4*(qgb)^2
-  +pga*(qga)^5*(qgb)^6
-  +(pga)^6*(pgb)^5*qgb
-}
-
-A7 <- function(pga, pgb) {
-  qgb <- 1 - pgb
-  qga <- 1 - pga
-  
[…]

### 2019-12-11 funs_new.R

@@ -1,149 +1,0 @@
-
-library(numbers)
-library(tidyverse)
-
-
-# Probability that A wins rally given A serves
-## 1 - pr = qr = prob B wins given A serves
-pr <- function(pwon, pserve) {
-  mean(pwon / pserve)
-}
-
-# Probability that A wins game given A serves
-## 1 - pg = qg = prob B wins given A serves
-pg <- function(pr) {
-  qr <- 1 - pr
-  
-  pr^4 * (1 + 4*qr + 10*qr^2) + 20*(pr*qr)^3 * pr^2 * (1 - 2*pr*qr)^-1
-}
-
-
-#equation 6-8
-pASij <- function(i, j, pAG, pBG) { #i , j , prob a wins given a served, prob b wins given b served
-  # initial conditions
-  if(i == 0 & j == 0) return(1)
-  if(i < 0) return(0)
-  if(j < 0) return(0)
-  
-  
-  
-  if( i == 7 & j==5){
-    return(pASij(6,5, pAG, pBG) *(1-pBG))
-  }
-  
-  
-  
-  # if(i == 6 & j == 6) {
-  #   s <- 0
-  #   
-  #   for(x in 0:4) {
-  #     s <- s + pASij(x, 6, pag, pbg) + pASij(6, x, pag, pbg)
-  #   }
-  #   
-  #   return(1 -
-  #     (s +
-  #        pASij(7,5, pag, pbg) +
-  #        pASij(5,7, pag, pbg)))
-  # }
-  
-  if(mod((i-1+j), 2) == 0) {
-    
-    if(j == 6 & i <= 5) return( pASij(i, j-1, pAG, pBG)*(1-pAG) )
-    
-    else if( i == 6 & j <= 5) return( pASij(i-1, j, pAG, pBG)*pAG )
-    
-    return( pASij(i-1, j, pAG, pBG)*pAG + pASij(i, j-1, pAG, pBG)*(1-pAG))
-    
-  } else {
-    
-    if(j == 6 & i <= 5) return( pASij(i, j-1, pAG, pBG)*pBG )
-    
-    else if( i == 6 & j <= 5) return( pASij(i-1, j, pAG, pBG)*(1-pBG) )
-    
-    return( pASij(i-1, j, pAG, pBG)*(1-pBG) + pASij(i, j-1, pAG, pBG)*pBG )
-    
-  }
-}
-
-
-
[…]

### 2019-12-11 Group1Prez.Rmd
Fixed picture
New Tourney Data

--- 2019-12-11 Group1Prez.Rmd
@@
 ## Game of Tennis
-![](tennis-scoring.jpg){ width=85% }\
+
+```{r,echo=FALSE, fig.align='center'}
+include_graphics("Scoring.jpg")
+```
 
@@
 Winner1 <- which(T1 == max(T1))
-#Winner1
-
-#T2<- table(base::sample(rownames(Tourney1_Women), 2000, prob = Tourney1_Women$Our.P.Winning.the.Tournement., replace = TRUE)) 
-#Winner2 <- which(T2 == max(T2))
-#Winner2
 
 ggplot(data.frame(T1)) +
-  geom_col(aes(x=Var1, y=Freq)) +
+  geom_col(aes(x=Var1, y=Freq/2000)) +
   xlab("Players") + 
+  ylab("P(Winning the Tournement") +
   ggtitle("Which Player Won the Tournement?")
@@
 Winner1 <- which(T1 == max(T1))
-#Winner1
 
-#T2<- table(base::sample(rownames(Tourney1_Men), 2000, prob = Tourney1_Men$Our.P.Winning.the.Tournement., replace = TRUE)) 
-#Winner2 <- which(T2 == max(T2))
-#Winner2
+ggplot(data.frame(T1)) +
+  geom_col(aes(x=Var1, y=Freq/2000)) +
+  xlab("Players") +
+  ylab("P(Win the Tournement)") +
+  ggtitle("Which Player Won the Tournement?")
+
+```
+
+## 2019 Wimbledon: Women
+
+```{r, warning=FALSE, echo=FALSE}
+WimWomen <- read_csv("2019 Womens Wimbledon.csv")
+
+WimWomen$`P(Winning a Rally)` <- WimWomen$`Points Won on Serve`/WimWomen$`Total Points Served`
+
+WimWomen <- as.data.frame(WimWomen)
+
+WimWomen$`P(Winning Tournement)`<- pTC(WimWomen[1,4][1], WimWomen[2,4][1],WimWomen[3,4][1],WimWomen[3,4][1],2)
+
+T1<- table(base::sample(WimWomen$Name, 2000, prob = WimWomen$`P(Winning a Rally)`, replace = TRUE))
+
+Winner1 <- which(T1 == max(T1))
+
+ggplot(data.frame(T1)) +
+  geom_col(aes(x=Var1, y=Freq/2000)) +
+  xlab("Players") +
+  ylab("P(Win the Tournement)")
+  ggtitle("Which Player Won the Tournement?")
+
+```
+
+## 2019 Wimbledon: Men
+
+```{r, warning=FALSE, echo=FALSE}
+WimMen <- read_csv("2019 Men's Wimbledon.csv")
+
+WimMen <- as.data.frame(WimMen)
+
+WimMen$`P(Winning a Rally)` <- WimMen$`Points Won on Serve`/ WimMen$`Total Points on Serve`
+
+WimMen$`P(Winning Tournement)`<- pTC(WimMen[1,4][1], WimMen[2,4][1],WimMen[3,4][1],WimMen[3,4][1],2)
+
+T1<- table(base::sample(WimMen$Name, 2000, prob = WimMen$`P(Winning a Rally)`, replace = TRUE))
+
+Winner1 <- which(T1 == max(T1))
 

### 2019-12-11 funs_new.R

@@ -110,7 +110,7 @@ ps <- function(pAR, pBR) {
     pASij(6,6, pag, pbg) * pT(pAR, pBR)
 }
 
-source('Probability of winning a set broken down .R')
+#source('Probability of winning a set broken down .R')
 
 
 #where pag is prob A wins a game given A served and 

### 2019-12-11 funs.R
Cleaning it up by deleting unused info

@@ -148,27 +148,3 @@ pTC <- function(pr1, pr2, pr3, pr4, numset) {
   
   p1 * p2
 }
-
-# 60 * (pg1)^3 * qg1^2 * pg2^2 * qg2^3 +
-#   40 * pg1^2 * qg1^3 * pg2 * qg2^4 +
-#   20 * pg1^4 * qg1 * pg2^3 * qg2^2 +
-#   5 * pg1 * qg1^4 * qg2^5 +
-#   pg1^5 * pg2^4 * qg2
-# 
-# 30 * pr1^2 * (1-pr1)^4 * pr2 * (1-pr2)^5 +
-#   pr1 * (1-pr1)^5 * (1-pr2)^6 +
-#   200 * pr1^4 * (1-pr1)^2 * pr2^3 * (1-pr2)^3 +
-#   75 * pr1^5 * (1-pr1) * pr2^4 * (1-pr2)^2 +
-#   150 * pr1^3 * (1-pr1)^3 * pr2^2 * (1-pr2)^4 +
-#   6 * pr1^6 * pr2^5 * (1-pr2)
-# 
-# s=0
-# for(i in 0:4) {
-#   s <- s + pASij(i, 6, pag, pbg) + pASij(6,i, pag, pbg)
-# }
-# 
-# 1 -
-#   (s +
-#      pASij(7,5, pag, pbg) +
-#      pASij(5,7, pag, pbg))
-

### 2019-12-11 funs.R
Delected source Probability of winning a set broken down

@@ -110,9 +110,6 @@ ps <- function(pAR, pBR) {
     pASij(6,6, pag, pbg) * pT(pAR, pBR)
 }
 
-source('Probability of winning a set broken down .R')
-
-
 #where pag is prob A wins a game given A served and 
 #pbg is prob B wins a game given B served
 

### 2019-12-11 Group1Prez.Rmd
Trying to get .rmd to knit
Corrected some errors More to come

@@
 ---
-title: "Group 1: Tennis "
+title: "Group 1: Predicting the Outcomes of Tennis Tournaments"
+subtitle: "A Monte Carlo Approach"
 author: "Olivia Beck, Emma Lewis, Ryan Volkert"
@@
 
-- It is noted that points in tennis are not iid for most purposes this is not a bad assumption as the divergence from iid is small
+- It is noted that points in tennis are not iid for most purposes
+  - This is not a bad assumption as the divergence from iid is small
 
-- Both two out of three and three out of five set matches were considered aloowing for 13-point tiebreaker in each set if needed
+- Both two out of three and three out of five set matches were considered allowing for 13-point tiebreaker in each set if needed
 
-## The Game of Tennis
+## The Rules of Tennis
 
@@
 
-## Game of Tennis
+## The Rules of Tennis
 
@@
 
-Where, $p_A^S(i,j)$ is defined recursivly as:
+Where, $p_A^S(i,j)$ is defined recursively as:
 
@@
 
-Where,  $p_A^T(i,j)$ is defined recursivly as:
+Where,  $p_A^T(i,j)$ is defined recursively as:
 
@@
 
-  - Men and Women semifinalists in the 2002 Wimbledon tournament
+  - Men and Women semifinalists in the 2002 Wimbledon tournament \pause
 
@@
 
-  - Men and Women semifinalists in the 2019 Wibledon tournament
+  - Men and Women semifinalists in the 2019 Wimbledon tournament
 
@@
 
-```{r, warning=FALSE, echo=FALSE}
+```{r, warning=FALSE, echo=FALSE, message=F}
 WimWomen <- read_csv("2019 Womens Wimbledon.csv")
@@
 
-T1<- table(base::sample(WimWomen$Name, 2000, prob = WimWomen$`P(Winning a Rally)`, replace = TRUE))
+T1 <- table(base::sample(WimWomen$Name, 2000, prob = WimWomen$`P(Winning a Rally)`, replace = TRUE))
 
@@
   xlab("Players") +
-  ylab("P(Win the Tournement)")
-  ggtitle("Which Player Won the Tournement?")
+  ylab("P(Win the Tournament)") +
+  ggtitle("Which Player Won the Tournament?")
 
@@
 
-```{r, warning=FALSE, echo=FALSE}
+```{r, warning=FALSE, echo=FALSE, message=F}
 WimMen <- read_csv("2019 Men's Wimbledon.csv")

### 2019-12-12 Group1Prez.Rmd
Forgot to save before last commit
Updated slides and added graphics

--- 2019-12-11 Group1Prez.Rmd
@@
 
-## Tournament Results: Women
+## 2002 U.S Open: Women
 ```{r, echo=FALSE}
@@
 
-## Tournament Results: Men
-```{r, echo=FALSE}
+## 2002 U.S Open: Women
+
+```{r,echo=FALSE, fig.align='center'}
+include_graphics("Serena.png")
+```
+
+## 2002 U.S Open: Men
+```{r, echo=FALSE, }
 Tourney1_Men = data.frame(`P(Winning a Rally)` = TDMen[,1],
@@
 
+##2002 U.S Open: Men
+
+```{r,echo=FALSE, fig.align='center'}
+include_graphics("Pete.png")
+```
+
 ## 2019 Wimbledon: Women
 
-```{r, warning=FALSE, echo=FALSE}
+```{r, warning=FALSE, echo=FALSE, message=FALSE}
 WimWomen <- read_csv("2019 Womens Wimbledon.csv")
@@
   xlab("Players") +
-  ylab("P(Win the Tournement)")
+  ylab("P(Win the Tournement)")+
   ggtitle("Which Player Won the Tournement?")
@@
 
+## 2019 Wimbledon: Women
+
+```{r,echo=FALSE, fig.align='center'}
+include_graphics("Simona.png")
+```
+
 ## 2019 Wimbledon: Men
 
-```{r, warning=FALSE, echo=FALSE}
+```{r, warning=FALSE, echo=FALSE, message=FALSE}
 WimMen <- read_csv("2019 Men's Wimbledon.csv")
@@
 ggplot(data.frame(T1)) +
-  geom_col(aes(x=Var1, y=Freq)) +
+  geom_col(aes(x=Var1, y=Freq/2000)) +
   xlab("Players") +
+   ylab("P(Win the Tournement)")+
   ggtitle("Which Player Won the Tournement?")
@@
 ```
+
+## 2019 Wimbledon: Men 
+```{r,echo=FALSE, fig.align='center'}
+include_graphics("Novak.png")
+```

### 2019-12-12 Group1Prez.Rmd

--- 2019-12-11 Group1Prez.Rmd
@@
 
+##2002 U.S Open: Men
+
+```{r,echo=FALSE, fig.align='center'}
+include_graphics("Pete.png")
+```
+
 ## 2019 Wimbledon: Women
@@
 ```{r, warning=FALSE, echo=FALSE, message=F}
+
 WimWomen <- read_csv("2019 Womens Wimbledon.csv")
@@
 
+## 2019 Wimbledon: Women
+
+```{r,echo=FALSE, fig.align='center'}
+include_graphics("Simona.png")
+```
+
 ## 2019 Wimbledon: Men
@@
 ```{r, warning=FALSE, echo=FALSE, message=F}
+
 WimMen <- read_csv("2019 Men's Wimbledon.csv")

### 2019-12-12 Group1Prez.Rmd
update
Finalizing presentation

@@
 library(knitr)
+opts_chunk$set(echo=FALSE)
 options(kableExtra.latex.load_packages = FALSE) 
@@
 
-- Project based off a paper by Paul K. Newton and Joseph B. Keller called Probability of Winning at Tennis 1. Theory and Data
+- Based on a paper by Paul K. Newton and Joseph B. Keller called *Probability of Winning at Tennis 1. Theory and Data*
 
@@
 
-- It is noted that points in tennis are not iid for most purposes
-  - This is not a bad assumption as the divergence from iid is small
+- It is noted that points in tennis are not iid for most purposes. This is not a bad assumption as the divergence from iid is small
 
@@
 
-- Set: A set consists of 6 games and is won by the player who reaches 6 games first
+- Set: A set is won by the player who wins 6 games first
 
@@
 
-- Matches: Best of 3 set (for women) or 5 sets (for men)
+- Matches: Best of 3 sets (for women) or 5 sets (for men)
 
@@
 
-$p_A^S(0,0) = 1$, $p_A^S(i,j) = 0$ if i<0 or j<0.
+$p_A^S(0,0) = 1$, $p_A^S(i,j) = 0$ if $i<0$ or $j<0$.
 
@@
 $$\text{P(A Winning the Tie Breaker | A Served Initially)} $$
-$$=p_A^T = \sum_{j=0}^5p_A^T(7,j) +  p_A^T(6,6)\sum_{n=1}^{\infty} p_A^T(n+2, n) $$ \pause
+$$=p_A^T = \sum_{j=0}^5p_A^T(7,j) +  p_A^T(6,6)p_A^Rq_B^R[1 - p_A^Rp_B^R - q_A^Rq_B^R]^{-1}$$ \pause
 
@@
 
-## Data being used 
+## Data
 Data used in paper:
@@
 ## 2002 U.S Open: Women
-```{r, echo=FALSE}
-Tourney1_Women = data.frame(`P(Winning a Rally)` = TDWomen[,1],
-                            `Paper P(Winning the Tournement)` = c(.2872, .3599, .0482, .3074))
+```{r, echo=FALSE, message=F, warning=F}
+W02 <- read_csv('2002 US Open tournament- Women.csv') %>%
+  filter(!is.na(Name)) %>%
+  mutate(pRally = NA)
+
+for(i in 1:4) {
+  W02$pRally[i] <- pr(as.numeric(W02[i,2]), as.numeric(W02[i,3]))
+}
+
+pRally <- as.numeric(W02$pRally)
+
+W02$pTC <- as.numeric(pTC(pRally[1], pRally[2], pRally[3], pRally[4], 2)) #c(.2872, .3599, .0482, .3074))
 #`Our P(Winning the Tournement )` =round( pTC(TDWomen[1,1],TDWomen[2,1],TDWomen[3,1],TDWomen[4,1], 2), 4)
 
-rownames(Tourney1_Women)<- c("S. Williams","L. Davenport",  "A. Mauresmo", "V. Williams")
-
-T1<- table(base::sample(rownames(Tourney1_Women), 2000, prob = Tourney1_Women$Paper.P.Winning.the.Tournement., replace = TRUE))
+T1<- table(base::sample(W02$Name, 2000, prob = W02$pTC, replace = TRUE))
 
@@
 ggplot(data.frame(T1)) +
-  geom_col(aes(x=Var1, y=Freq/2000)) +
+  geom_col(aes(x=Var1, y=Freq)) +
   xlab("Players") + 
-  ylab("P(Winning the Tournement") +
-  ggtitle("Which Player Won the Tournement?")
+  ylab("Number of Times Won") +
+  ggtitle("Which Player Won the Tournament?",
+          subtitle = "2002 Women's US Open")
 
@@
 ## 2002 U.S Open: Men
-```{r, echo=FALSE, }
-Tourney1_Men = data.frame(`P(Winning a Rally)` = TDMen[,1],
-                            `Paper P(Winning the Tournement)` = c(.6747, .0851, .0945, .1457))
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+mOpen <- read_csv('2002 US Open- Men.csv') %>%
+  filter(!is.na(Name)) %>%
+  mutate(pRally = NA)
+
+for(i in 1:4) {
+  mOpen$pRally[i] <- pr(as.numeric(mOpen[i,2]), as.numeric(mOpen[i,3]))
+}
+
+pRally <- as.numeric(mOpen$pRally)
+
+mOpen$pTC <- as.numeric(pTC(pRally[1], pRally[2], pRally[3], pRally[4], 3))
 #`Our P(Winning the Tournement )` =round( pTC(TDMen[1,1],TDMen[2,1],TDMen[3,1],TDMen[4,1], 2), 4)
 
-rownames(Tourney1_Men)<- c("P. Sampras","S. Schalken",  "A. Agassi", "L. Hewitt")
+T2<- table(base::sample(mOpen$Name, 2000, prob = mOpen$pTC, replace = TRUE))
 
-T1<- table(base::sample(rownames(Tourney1_Men), 2000, prob = Tourney1_Men$Paper.P.Winning.the.Tournement., replace = TRUE))
+Winner2 <- which(T2 == max(T2))
 
-Winner1 <- which(T1 == max(T1))
-
-ggplot(data.frame(T1)) +
-  geom_col(aes(x=Var1, y=Freq/2000)) +
+ggplot(data.frame(T2)) +
+  geom_col(aes(x=Var1, y=Freq)) +
   xlab("Players") +
-  ylab("P(Win the Tournement)") +
-  ggtitle("Which Player Won the Tournement?")
+  ylab("Number of Times Won") +
+  ggtitle("Which Player Won the Tournament?",
+          subtitle = "2002 Men's US Open")
 
@@
 
-##2002 U.S Open: Men
+## 2002 U.S Open: Men
 
@@
 include_graphics("Pete.png")
+```
+
+## 2002 Wimbledon: Women
+
+```{r, message=F, warning=F}
+wWim02 <- read_csv('2002 Wimbledon -Women.csv') %>%
+  filter(!is.na(Name)) %>%
+  mutate(pRally = NA)
+
+for(i in 1:4) {
+  wWim02$pRally[i] <- pr(as.numeric(wWim02[i,2]), as.numeric(wWim02[i,3]))
+}
+
+pRally <- as.numeric(wWim02$pRally)
+
+wWim02$pTC <- as.numeric(pTC(pRally[1], pRally[2], pRally[3], pRally[4], 2))
+
+T3 <- table(base::sample(wWim02$Name, 2000, prob = wWim02$pTC, replace = TRUE))
+
+ggplot(data.frame(T3)) +
+  geom_col(aes(x=Var1, y=Freq)) +
+  xlab('Players') +
+  ylab('Number of Times Won') +
+  ggtitle('Which Player Won the Tournament?',
+          subtitle = "2002 Women's Wimbledon")
+```
+
+## 2002 Wimbledon: Women
+
+```{r, fig.align='center'}
+include_graphics('Serena2.png')
+```
+
+## 2002 Wimbledon: Men
+
+```{r, message=F, warning=F}
+mWim02 <- read_csv('2002 Wimbledon- Men.csv') %>%
+  filter(!is.na(Name)) %>%
+  mutate(pRally = NA)
+
+for(i in 1:4) {
+  mWim02$pRally[i] <- pr(as.numeric(mWim02[i,2]), as.numeric(mWim02[i,3]))
+}
+
+pRally <- as.numeric(mWim02$pRally)
+
+mWim02$pTC <- as.numeric(pTC(pRally[1], pRally[2], pRally[3], pRally[4], 2))
+
+T4 <- table(base::sample(mWim02$Name, 2000, prob = mWim02$pTC, replace = TRUE))
+
+ggplot(data.frame(T4)) +
+  geom_col(aes(x=Var1, y=Freq)) +
+  xlab('Players') +
+  ylab('Number of Times Won') +
+  ggtitle('Which Player Won the Tournament?',
+          subtitle = "2002 Men's Wimbledon")
+```
+
+## 2002 Wimbledon: Men
+
+```{r, fig.align='center'}
+include_graphics('Hewitt.png')
 ```
@@
 
-WimWomen <- read_csv("2019 Womens Wimbledon.csv")
+wWim19 <- read_csv('2019 Womens Wimbledon.csv') %>%
+  filter(!is.na(Name)) %>%
+  mutate(pRally = NA)
 
-WimWomen$`P(Winning a Rally)` <- WimWomen$`Points Won on Serve`/WimWomen$`Total Points Served`
+for(i in 1:4) {
+  wWim19$pRally[i] <- pr(as.numeric(wWim19[i,2]), as.numeric(wWim19[i,3]))
+}
 
-WimWomen <- as.data.frame(WimWomen)
+pRally <- as.numeric(wWim19$pRally)
 
-WimWomen$`P(Winning Tournement)`<- pTC(WimWomen[1,4][1], WimWomen[2,4][1],WimWomen[3,4][1],WimWomen[3,4][1],2)
+wWim19$pTC <- as.numeric(pTC(pRally[1], pRally[2], pRally[3], pRally[4], 2))
 
-T1 <- table(base::sample(WimWomen$Name, 2000, prob = WimWomen$`P(Winning a Rally)`, replace = TRUE))
+T4 <- table(base::sample(wWim19$Name, 2000, prob = wWim19$pTC, replace = TRUE))
 
-Winner1 <- which(T1 == max(T1))
-
-ggplot(data.frame(T1)) +
-  geom_col(aes(x=Var1, y=Freq/2000)) +
-  xlab("Players") +
-  ylab("P(Win the Tournament)") +
-  ggtitle("Which Player Won the Tournament?")
-
+ggplot(data.frame(T4)) +
+  geom_col(aes(x=Var1, y=Freq)) +
+  xlab('Players') +
+  ylab('Number of Times Won') +
+  ggtitle('Which Player Won the Tournament?',
+          subtitle = "2019 Women's Wimbledon")
 ```
@@
 
-WimMen <- read_csv("2019 Men's Wimbledon.csv")
+mWim19 <- read_csv("2019 Men's Wimbledon.csv") %>%
+  filter(!is.na(Name)) %>%
+  mutate(pRally = NA)
 
-WimMen <- as.data.frame(WimMen)
+for(i in 1:4) {
+  mWim19$pRally[i] <- pr(as.numeric(mWim19[i,2]), as.numeric(mWim19[i,3]))
+}
 
-WimMen$`P(Winning a Rally)` <- WimMen$`Points Won on Serve`/ WimMen$`Total Points on Serve`
+pRally <- as.numeric(mWim19$pRally)
 
-WimMen$`P(Winning Tournement)`<- pTC(WimMen[1,4][1], WimMen[2,4][1],WimMen[3,4][1],WimMen[3,4][1],2)
+mWim19$pTC <- as.numeric(pTC(pRally[1], pRally[2], pRally[3], pRally[4], 2))
 
-T1<- table(base::sample(WimMen$Name, 2000, prob = WimMen$`P(Winning a Rally)`, replace = TRUE))
+T5 <- table(base::sample(mWim19$Name, 2000, prob = mWim19$pTC, replace = TRUE))
 
-Winner1 <- which(T1 == max(T1))
-
-ggplot(data.frame(T1)) +
-  geom_col(aes(x=Var1, y=Freq/2000)) +
-  xlab("Players") +
-   ylab("P(Win the Tournement)")+
-  ggtitle("Which Player Won the Tournement?")
-
+ggplot(data.frame(T5)) +
+  geom_col(aes(x=Var1, y=Freq)) +
+  xlab('Players') +
+  ylab('Number of Times Won') +
+  ggtitle('Which Player Won the Tournament?',
+          subtitle = "2002 Men's Wimbledon")
 ```
@@
 ## 2019 Wimbledon: Men
+
 ```{r,echo=FALSE, fig.align='center'}

### 2019-12-12 Group1Prez.Rmd
Final Prez

@@
 
-```{r,echo=FALSE, fig.align='center'}
-include_graphics("Serena.png")
-```
+\centerline{\includegraphics[height=2in]{Serena.png}}
 
@@
 ggplot(data.frame(T2)) +
-  geom_col(aes(x=Var1, y=Freq)) +
+  geom_col(aes(x=Var1, y=Freq/2000)) +
   xlab("Players") +
-  ylab("Number of Times Won") +
+  ylab("Proportion of Times Won") +
   ggtitle("Which Player Won the Tournament?",
@@
 
-```{r,echo=FALSE, fig.align='center'}
-include_graphics("Pete.png")
-```
+\centerline{\includegraphics[height=2in]{Pete.png}}
 
@@
 ggplot(data.frame(T3)) +
-  geom_col(aes(x=Var1, y=Freq)) +
+  geom_col(aes(x=Var1, y=Freq/2000)) +
   xlab('Players') +
-  ylab('Number of Times Won') +
+  ylab('Proportion of Times Won') +
   ggtitle('Which Player Won the Tournament?',
@@
 
-```{r, fig.align='center'}
-include_graphics('Serena2.png')
-```
+\centerline{\includegraphics[height=2in]{Serena2.png}}
 
@@
 
-mWim02$pTC <- as.numeric(pTC(pRally[1], pRally[2], pRally[3], pRally[4], 2))
+mWim02$pTC <- as.numeric(pTC(pRally[1], pRally[2], pRally[3], pRally[4], 3))
 
@@
 ggplot(data.frame(T4)) +
-  geom_col(aes(x=Var1, y=Freq)) +
+  geom_col(aes(x=Var1, y=Freq/2000)) +
   xlab('Players') +
-  ylab('Number of Times Won') +
+  ylab('Proportion of Times Won') +
   ggtitle('Which Player Won the Tournament?',
@@
 
-```{r, fig.align='center'}
-include_graphics('Hewitt.png')
-```
+\centerline{\includegraphics[height=2in]{Hewitt.png}}
 
@@
 
-```{r,echo=FALSE, fig.align='center'}
-include_graphics("Simona.png")
-```
+\centerline{\includegraphics[height=2in]{Simona.png}}
 
@@
 
-mWim19$pTC <- as.numeric(pTC(pRally[1], pRally[2], pRally[3], pRally[4], 2))
+mWim19$pTC <- as.numeric(pTC(pRally[1], pRally[2], pRally[3], pRally[4], 3))
 
@@
 ggplot(data.frame(T5)) +
-  geom_col(aes(x=Var1, y=Freq)) +
+  geom_col(aes(x=Var1, y=Freq/2000)) +
   xlab('Players') +
-  ylab('Number of Times Won') +
+  ylab('Proportion of Times Won') +
   ggtitle('Which Player Won the Tournament?',
@@
 
-```{r,echo=FALSE, fig.align='center'}
-include_graphics("Novak.png")
-```
+\centerline{\includegraphics[height=2in]{Novak.png}}

### 2019-12-17 PaperDraft.Rmd
Added Methods, Reproducibility, bibtex, and limitations

@@
 ---
-title: "Draft"
-author: " "
-date: "November 11, 2019"
+title: "Tennis"
+author: "Olivia Beck, Emma Lewis, Ryan Volkert"
+date: "Decemeber 19, 2019"
 output: pdf_document
+bibliography: bibliography.bib
 ---
@@
 knitr::opts_chunk$set(echo = FALSE)
+source("funs.R")
+library(knitr)
+library(kableExtra)
+library(tidyverse)
+set.seed(400)
 ```
+
+### Introduction
+
+For our report, we replicated the methods outlined in @Tennis for predicting the outcome of a tennis tourement.
 
@@
 
-- How likely are the players to win the tournament?
-
 The probability of winning a game, a set, and a match in tennis are calculated based on the each players probability of winning a point on a serve.
-This paper and the reference paper, The Probability of Winning at Tennis 1.
-Theory and Data written by Paul K.
-Newton and Joseph B.
-Keller both make the assumption that each serve is an independently and identically distributed (iid) random variable.
-This assumption has been made in other reports relating to the probability of winning a game in other racket sports and even though serves in tennis are not actually iid random variables for most purposes this is not a bad assumption as the divergence from iid is small.
+This paper and the reference paper,@Tennis both make the assumption that each serve is an independently and identically distributed (iid) random variable.
+This assumption has been made in other reports relating to the probability of winning a game in other racket sports and even though serves in tennis are not iid random variables in reality.
+For most purposes this is not an outragous assumption as the divergence from iid is small.
 
@@
 
-- Where we got our data
+Data for the 2002 Wimbledon for men's and women's as well as 2002 US Open for men's and women's was provided in @Tennis. Data for 2019 Wimbledon for men's and women's was found at @2019data.
 
-- Probability of winning a game, set, match
+The probability of winning a game, set, match, and tournament is derived in @Tennis as follows:
+
+ - P(A Winning a Rally | A Served)
+
+ $$p_A^R = \frac{\text{Points Won On Serve}}{\text{Points Served}}$$
+
+- P(A Winning a Game | A Served)
+
+$$p_A^G = (p_A^R)^4[1+4q_A^R+10(q_A^R)^2] +20(p_A^Rq_A^R)^3(p_A^R)^2[1-2p_A^Rq_A^R]^{-1}$$
+
+- P(A Winnning a Set | A Served)
+
+$$p_A^S =\sum_{j=0}^4p_A^S(6,j) + p_A^S(7,5) + p_A^S(6,6)p_A^T$$
+
+- P(A Winning the Tie Breaker | A Served Initially)
+
+$$p_A^T = \sum_{j=0}^5p_A^T(7,j) +  p_A^T(6,6)p_A^Rq_B^R[1 - p_A^Rp_B^R - q_A^Rq_B^R]^{-1}$$
+
+- P(Winning a Women's Match, Best of 3)
+
+$$p_A^M = (p_A^S)^2 + 2(p_A^S)^2p_B^S$$
+
+- P(Winning a Men's Match, Best of 5)
+
+$$p_A^M = (p_A^S)^3 + 3(p_A^S)^3p_B^S + 6(p_A^S)^3(p_B^S)^2$$
+
+<!-- Need to add P(winning the Tournement) -->
+
+Where, $p_A^S(i,j)$ is defined recursively as:
+
+$p_A^S(0,0) = 1$, $p_A^S(i,j) = 0$ if $i<0$ or $j<0$.
+
+- if i+j -1 is even: $p_A^S(i,j) = p_A^S(i-1,j)p_A^G + p_A^S(i, j-1)q_A^G$
+
+    - omit i-1 term if j=6 and i<6
+
+    - omit j-1 term if i=6 and j<6
+
+- if i+j -1 is odd: $p_A^S(i,j) = p_A^S(i-1,j)q_B^G + p_A^S(i, j-1)p_B^G$
+
+    - omit i-1 term if j=6 and i<6
+
+    - omit j-1 term if i=6 and j<6.
+
+And,  $p_A^T(i,j)$ is defined recursively as:
+
+$p_A^T(0,0) = 1$, $p_A^T(i,j) = 0$ if i<0 or j<0.
+
+- if $i+j -1 \mod 4 \equiv 0 \; \text{or} \;3$: $p_A^S(i,j) = p_A^T(i-1,j)p_A^R + p_A^T(i, j-1)q_A^R$
+
+    - omit i-1 term if j=7 and i<7
+
+    - omit j-1 term if i=7 and j<7
+
+- if $i+j -1 \mod 4 \equiv 1 \; \text{or} \; 2$: $p_A^T(i,j) = p_A^T(i-1,j)q_B^R + p_A^T(i, j-1)p_B^R$
+
+    - omit i-1 term if j=7 and i<7
+
+    - omit j-1 term if i=7 and j<7
 
@@
 
-- Reproduce data in paper
+First we will consider data from the 2002 US Open for both men's and women's.
+We want to reproduce the probability of winning a game.
+Table 1 compares the empirical probablity of winning a game versus the theoretical probability of winning a game calculated in @Tennis verus the probability of winning a game that we calculated for the 4 semi finalists in this tournament.
+We can see that the vales that we caluculated and the values calculated in @Tennis are the same.
+These values do differ slightly from the empiricial probabilities.
+Table 2 outlines the same comparisons except for the men's 2002 US Open.
+
+```{r, echo = FALSE}
+
+TDWomen <- as.data.frame(matrix(0, nrow = 4, ncol = 3))
+
+colnames(TDWomen) <- c("P(Win a Rally)", "Empirical P(Win a Game)", "Paper P(Win a Game)" )
+
+TDWomen[1, ] <- c(0.69, 0.71, 0.89)
+TDWomen[2, ] <- c(0.63, 0.80, 0.79)
+TDWomen[3, ] <- c(0.65, 0.85, 0.83)
+TDWomen[4, ] <- c(0.63, 0.77, 0.79)
+
+OurDatWomen <- as.matrix(round(c(pg(TDWomen[1,1]), pg(TDWomen[2,1]), pg(TDWomen[3,1]), pg(TDWomen[4,1])),2))
+
+TDWomen$`Our P(Win a Game)` <-(OurDatWomen)
+
+rownames(TDWomen) <- c("S. Williams", "V. Williams", "L. Davenport", "A. Mauresmo")
+
+kable(TDWomen, format = "latex", booktabs = TRUE, caption = "Data for the Womens Semifinalists in the 2002 U.S. Open Tournament
+")%>%
+          kable_styling(latex_options = "scale_down")
+
+```
+
+```{r, echo = FALSE}
+
+TDMen<- as.data.frame(matrix(0, nrow = 4, ncol = 3))
+
+colnames(TDMen) <- c("P(Win a Rally)", "Empirical P(Win a Game)", "Paper P(Win a Game)" )
+
+TDMen[1, ] <- c(0.73, 0.95, 0.93)
+TDMen[2, ] <- c(0.66, 0.87, 0.85)
+TDMen[3, ] <- c(0.67, 0.85, 0.86)
+TDMen[4, ] <- c(0.68, 0.90, 0.88)
+
+OurDatWMen <- as.matrix(round(c(pg(TDMen[1,1]), pg(TDMen[2,1]), pg(TDMen[3,1]), pg(TDMen[4,1])),2))
+
+TDMen$`Our P(Win a Game)` <-(OurDatWMen)
+
+rownames(TDMen) <- c("P. Sampras", "A. Agassi", "L. Hewitt", "S. Schalken")
+
+kable(TDMen, format = "latex", booktabs = TRUE, caption = "Data for the Mens Semifinalists in the 2002 U.S. Open Tournament
+")%>%
+          kable_styling(latex_options = "scale_down")
+
+```
+
+Next, we want to comapare the probability of winning a tournement.
+@Tennis does not provide their predictions of tournament winners, only their probabilies comparted to what actually happened in the tournement.
+The paper also only considers the 4 semifinalists when predicting the tournement, so we will as well.
+
+We fist look at 2002 US Open's Womens tournement for the 4 semi finalists.
+We calculate the probability each semi finalist has of winning the tournament, then we sample one player to win the tournament with the probabilites we calculated.
+Figure 1 shows the results from 2000 tournements played with these 4 semi finalists.
+From our simlations we predict that S.
+Williams wins the tournement, and in fact she did win this tournement.
+
+```{r, echo=FALSE, message=F, warning=F}
+W02 <- read_csv('2002 US Open tournament- Women.csv') %>%
+  filter(!is.na(Name)) %>%
+  mutate(pRally = NA)
+
+for(i in 1:4) {
+  W02$pRally[i] <- pr(as.numeric(W02[i,2]), as.numeric(W02[i,3]))
+}
+
+pRally <- as.numeric(W02$pRally)
+
+W02$pTC <- as.numeric(pTC(pRally[1], pRally[2], pRally[3], pRally[4], 2))
+
+T1<- table(base::sample(W02$Name, 2000, prob = W02$pTC, replace = TRUE))
+
+Winner1 <- which(T1 == max(T1))
+
+ggplot(data.frame(T1)) +
+  geom_col(aes(x=Var1, y=Freq/2000)) +
+  xlab("Players") + 
+  ylab("Number of Times Won") +
+  ggtitle("Figure 1",
+          subtitle = "2002 Women's US Open")
+
+```
+Similarly, we want to consider the 2002 US Open for the men's semifinalists.
+Using the same method outline above, we can see in Figure 2 that we predict P.
+Sampras to win the tournement, and in fact he did win this tournament.
+
+```{r, echo=FALSE, message=FALSE, warning=FALSE}
+mOpen <- read_csv('2002 US Open- Men.csv') %>%
+  filter(!is.na(Name)) %>%
+  mutate(pRally = NA)
+
+for(i in 1:4) {
+  mOpen$pRally[i] <- pr(as.numeric(mOpen[i,2]), as.numeric(mOpen[i,3]))
+}
+
+pRally <- as.numeric(mOpen$pRally)
+
+mOpen$pTC <- as.numeric(pTC(pRally[1], pRally[2], pRally[3], pRally[4], 3))
+T2<- table(base::sample(mOpen$Name, 2000, prob = mOpen$pTC, replace = TRUE))
+
+Winner2 <- which(T2 == max(T2))
+
+ggplot(data.frame(T2)) +
+  geom_col(aes(x=Var1, y=Freq/2000)) +
+  xlab("Players") +
+  ylab("Proportion of Times Won") +
+  ggtitle("Figure 2",
+          subtitle = "2002 Men's US Open")
+
+```
+
+Next, we consider data from the 2002 Wimbeldon.
+The probability of winning a rally for the 4 semifinalists for both women's and men's can be found in Table 3.
+Figure 3 shows the results for the 2002 Women's Wimbledon.
+We predict that V.
+Williams wins, but in reality S.
+Williams had an upset win.
+Some speculations as to why we predicted incorrectly can be found in the Limitations section.
+Figure 4 shows the same methods as Figure 3, but for the men's semi finalists.
+We predict L.
+Hewitt to win the tournament, and in fact he does.
+
+```{r, echo = FALSE}
+
+Wimb2002 <- as.data.frame(matrix(0, nrow = 4,  ncol = 4))
+
+colnames(Wimb2002) <- c("Women" ,"P(Win a Rally)","Men" ,"P(Win a Rally)" )
+
+Wimb2002[,1] <- c( "S. Williams", "V. Williams", "J.Henin", "A. Mauresmo")
+
+Wimb2002[,2]<- c( 0.71, 0.67, 0.59, 0.64)
+
+Wimb2002[,3] <-  c( "L. Hewitt", "D. Nalbandian", "T. Henman", "X. Malisse")
+
+Wimb2002[ ,4]<- c(0.77, 0.61, 0.67, 0.67)
+
+kable(Wimb2002, format = "latex", booktabs = TRUE, caption = "Data for the Semifinalists in the 2002 Wimbledon Tournament
+")%>%
+          kable_styling(latex_options = "scale_down")
+
+```
+```{r, message=F, warning=F}
+wWim02 <- read_csv('2002 Wimbledon -Women.csv') %>%
+  filter(!is.na(Name)) %>%
+  mutate(pRally = NA)
+
+for(i in 1:4) {
+  wWim02$pRally[i] <- pr(as.numeric(wWim02[i,2]), as.numeric(wWim02[i,3]))
+}
+
+pRally <- as.numeric(wWim02$pRally)
+
+wWim02$pTC <- as.numeric(pTC(pRally[1], pRally[2], pRally[3], pRally[4], 2))
+
+T3 <- table(base::sample(wWim02$Name, 2000, prob = wWim02$pTC, replace = TRUE))
+
+ggplot(data.frame(T3)) +
+  geom_col(aes(x=Var1, y=Freq/2000)) +
+  xlab('Players') +
+  ylab('Proportion of Times Won') +
+  ggtitle('Figure 3',
+          subtitle = "2002 Women's Wimbledon")
+```
+```{r, message=F, warning=F}
+mWim02 <- read_csv('2002 Wimbledon- Men.csv') %>%
+  filter(!is.na(Name)) %>%
+  mutate(pRally = NA)
+
+for(i in 1:4) {
+  mWim02$pRally[i] <- pr(as.numeric(mWim02[i,2]), as.numeric(mWim02[i,3]))
+}
+
+pRally <- as.numeric(mWim02$pRally)
+
+mWim02$pTC <- as.numeric(pTC(pRally[1], pRally[2], pRally[3], pRally[4], 3))
+
+T4 <- table(base::sample(mWim02$Name, 2000, prob = mWim02$pTC, replace = TRUE))
+
+ggplot(data.frame(T4)) +
+  geom_col(aes(x=Var1, y=Freq/2000)) +
+  xlab('Players') +
+  ylab('Proportion of Times Won') +
+  ggtitle('Figure 4 ',
+          subtitle = "2002 Men's Wimbledon")
+```
 
@@
 
-- Same thing with new tournament
+For our extension, we ran the same method on data from the 2019 Wimbledon Tournament for both men's and women's.
+The data for probability of winning a rally can be found in Table 4.
+As seen in Figure 5, we predict that B.
+Strycoa wins the tournament, but S.
+Halep actually won the 2019 Women's Wimbledon.
+Similarly, in Figure 6 we predict that Rodger Federer and Rafeal Nadal essentially have an equal probability of winning the tournement, but it was Novak Djokovic who actually won the tournement.
+Again, the discrepencies between who won the tourment and what we predicted are discussed in the limitations section.
+```{r, echo =FALSE, warning=FALSE}
+#Women
+wWim19 <- read_csv('2019 Womens Wimbledon.csv') %>%
+  filter(!is.na(Name)) %>%
+  mutate(pRally = NA)
 
-- Maybe with new method if we have time
+for(i in 1:4) {
+  wWim19$pRally[i] <- pr(as.numeric(wWim19[i,2]), as.numeric(wWim19[i,3]))
+}
+
+pRally <- as.numeric(wWim19$pRally)
+
+wWim19$pTC <- as.numeric(pTC(pRally[1], pRally[2], pRally[3], pRally[4], 2))
+
+#Men
+mWim19 <- read_csv("2019 Men's Wimbledon.csv") %>%
+  filter(!is.na(Name)) %>%
+  mutate(pRally = NA)
+
+for(i in 1:4) {
+  mWim19$pRally[i] <- pr(as.numeric(mWim19[i,2]), as.numeric(mWim19[i,3]))
+}
+
+pRally <- as.numeric(mWim19$pRally)
+
+mWim19$pTC <- as.numeric(pTC(pRally[1], pRally[2], pRally[3], pRally[4], 3))
+
+#table
+Tab1 <- wWim19[c(1,4) ]
+colnames(Tab1) <- c("Women", "P(Winning a Rally)")
+
+Tab2 <- wWim19[c(1,4) ]
+colnames(Tab2) <- c("Men", "P(Winning a Rally)")
+
+Tab<-cbind(Tab1, Tab2)
+kable(Tab, format = "latex", booktabs = TRUE, caption = "Data for the Semifinalists in the 2019 Wimbledon Tournament
+")%>%
+          kable_styling(latex_options = "scale_down")
+
+```
+
+```{r, warning=FALSE, echo=FALSE, message=F}
+
+T4 <- table(base::sample(wWim19$Name, 2000, prob = wWim19$pTC, replace = TRUE))
+
+ggplot(data.frame(T4)) +
+  geom_col(aes(x=Var1, y=Freq/2000)) +
+  xlab('Players') +
+  ylab('Proportion of Times Won') +
+  ggtitle('Figure 5',
+          subtitle = "2019 Women's Wimbledon")
+```
+
+```{r, warning=FALSE, echo=FALSE, message=F}
+
+T5 <- table(base::sample(mWim19$Name, 2000, prob = mWim19$pTC, replace = TRUE))
+
+ggplot(data.frame(T5)) +
+  geom_col(aes(x=Var1, y=Freq/2000)) +
+  xlab('Players') +
+  ylab('Proportion of Times Won') +
+  ggtitle('Figure 6',
+          subtitle = "2002 Men's Wimbledon")
+```
+
+### Conclusions
+
+### Limitations
+
+When a tennis tournament is played, the empirical probability of winning a point on serve changes every time a rally is completed.
+This report does not take that into account.
+For this report we used previous tournament data to calculate the probability each player had of winning the tournament.
+Our data did not update as the tournament progressed.
+There is one major draw back to this approach.
+Our method only considers how a player was performing before the tournament and does not consider how they are performing during the tournament.
+This is one reason we see discrepancies between our predicted tournament winner and the actual winner of the tournament.
+For example, in the 2002 Women’s Wimbledon, Venus Williams was predicted to win, as she had the highest probability of winning a rally, but Serena Williams actually won the tournament.
+This is in part due to the discrepancies between how the players performed before the tournament and how they preformed during the tournament.
+Serena Williams performed much better during the tournament than she did leading up to it.
+One way to improve our predictions is to update our probabilities each time a rally is conducted.
+
+When a player plays well during a tournament, it gives them momentum which is important to winning in any sporting event.
+This report also did not take momentum into account.
+We assumed that all rallies were iid, but in reality, this is not the case.
+@Tennis assumes that the difference between iid and non-iid rallies is so small that for their purposes, and for ours, they assume that all rallies are iid.
+@noniid considers predictions for winning a tournament where rallies are non-iid.
 

### 2019-12-17 Group1Prez.Rmd
Cleaned Up

@@
 ggplot(data.frame(T1)) +
-  geom_col(aes(x=Var1, y=Freq)) +
+  geom_col(aes(x=Var1, y=Freq/2000)) +
   xlab("Players") + 

### 2019-12-18 PaperDraft.Rmd
changing positions of figures

@@
 output: pdf_document
+header - input: 
+  - \usepackage{float}
 bibliography: bibliography.bib
+
 ---
@@
 
-```{r, echo = FALSE}
+Next, we want to comapare the probability of winning a tournement.
+@Tennis does not provide their predictions of tournament winners, only their probabilies comparted to what actually happened in the tournement.
+The paper also only considers the 4 semifinalists when predicting the tournement, so we will as well.
+
+```{r, echo = FALSE, fig.pos="H"}
 
@@
 
-```{r, echo = FALSE}
+```{r, echo = FALSE, fig.pos="H"}
 
@@
 
-Next, we want to comapare the probability of winning a tournement.
-@Tennis does not provide their predictions of tournament winners, only their probabilies comparted to what actually happened in the tournement.
-The paper also only considers the 4 semifinalists when predicting the tournement, so we will as well.
-
-We fist look at 2002 US Open's Womens tournement for the 4 semi finalists.
-We calculate the probability each semi finalist has of winning the tournament, then we sample one player to win the tournament with the probabilites we calculated.
-Figure 1 shows the results from 2000 tournements played with these 4 semi finalists.
-From our simlations we predict that S.
-Williams wins the tournement, and in fact she did win this tournement.
-
-```{r, echo=FALSE, message=F, warning=F}
+```{r, echo=FALSE, message=F, warning=F, fig.pos="H"}
 W02 <- read_csv('2002 US Open tournament- Women.csv') %>%
@@
 ```
+
+We fist look at 2002 US Open's Womens tournement for the 4 semi finalists.
+We calculate the probability each semi finalist has of winning the tournament, then we sample one player to win the tournament with the probabilites we calculated.
+Figure 1 shows the results from 2000 tournements played with these 4 semi finalists.
+From our simlations we predict that S.
+Williams wins the tournement, and in fact she did win this tournement.
+
 Similarly, we want to consider the 2002 US Open for the men's semifinalists.
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE}
+```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
 mOpen <- read_csv('2002 US Open- Men.csv') %>%
@@
 ```
-```{r, message=F, warning=F}
+```{r, message=F, warning=F, fig.pos="H"}
 wWim02 <- read_csv('2002 Wimbledon -Women.csv') %>%
@@
 ```
-```{r, message=F, warning=F}
+```{r, message=F, warning=F, fig.pos="H"}
 mWim02 <- read_csv('2002 Wimbledon- Men.csv') %>%
@@
 Again, the discrepencies between who won the tourment and what we predicted are discussed in the limitations section.
-```{r, echo =FALSE, warning=FALSE}
+```{r, echo =FALSE, warning=FALSE, fig.pos="H", message=FALSE}
 #Women
@@
 
-```{r, warning=FALSE, echo=FALSE, message=F}
+```{r, warning=FALSE, echo=FALSE, message=F, fig.pos="H"}
 

### 2019-12-18 PaperDraft.Rmd
Added ToC

@@
 
+\newpage
+\tableofcontents
+\listoffigures
+\listoftables
+\newpage
+
 ```{r setup, include=FALSE}
@@
 
-### Introduction
+# Introduction
 
@@
 
-### Motivation
+# Motivation
 
@@
 
-### Methods
+# Methods
 
@@
 
-### Reproducability
+# Reproducability
 
@@
 
-```{r, echo=FALSE, message=F, warning=F, fig.pos="H"}
+```{r, echo=FALSE, message=F, warning=F, fig.pos="H", fig.cap = "2002 Women's US Open"}
 W02 <- read_csv('2002 US Open tournament- Women.csv') %>%
@@
   ylab("Number of Times Won") +
-  ggtitle("Figure 1",
-          subtitle = "2002 Women's US Open")
+  ggtitle("2002 Women's US Open")
 
@@
 
-```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H"}
+```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap = "2002 Men's US Open"}
 mOpen <- read_csv('2002 US Open- Men.csv') %>%
@@
   ylab("Proportion of Times Won") +
-  ggtitle("Figure 2",
-          subtitle = "2002 Men's US Open")
+  ggtitle("2002 Men's US Open")
 
@@
 ")%>%
-          kable_styling(latex_options = "scale_down")
+          kable_styling(full_width = T)
 
 ```
-```{r, message=F, warning=F, fig.pos="H"}
+```{r, message=F, warning=F, fig.pos="H", fig.cap = "2002 Women's Wimbledon"}
 wWim02 <- read_csv('2002 Wimbledon -Women.csv') %>%
@@
   ylab('Proportion of Times Won') +
-  ggtitle('Figure 3',
-          subtitle = "2002 Women's Wimbledon")
+  ggtitle("2002 Women's Wimbledon")
 ```
-```{r, message=F, warning=F, fig.pos="H"}
+```{r, message=F, warning=F, fig.pos="H", fig.cap = "2002 Men's Wimbledon"}
 mWim02 <- read_csv('2002 Wimbledon- Men.csv') %>%
@@
   ylab('Proportion of Times Won') +
-  ggtitle('Figure 4 ',
-          subtitle = "2002 Men's Wimbledon")
+  ggtitle("2002 Men's Wimbledon")
 ```
 
-### Extension
+# Extension
 
@@
 ")%>%
-          kable_styling(latex_options = "scale_down")
+          kable_styling(full_width = T)
 
@@
 
-```{r, warning=FALSE, echo=FALSE, message=F, fig.pos="H"}
+```{r, warning=FALSE, echo=FALSE, message=F, fig.pos="H", fig.cap = "2019 Women's Wimbledon"}
 
@@
   ylab('Proportion of Times Won') +
-  ggtitle('Figure 5',
-          subtitle = "2019 Women's Wimbledon")
+  ggtitle("2019 Women's Wimbledon")
 ```
 
-```{r, warning=FALSE, echo=FALSE, message=F, fig.pos="H"}
+```{r, warning=FALSE, echo=FALSE, message=F, fig.pos="H", fig.cap = "2019 Men's Wimbledon"}
 
@@
   ylab('Proportion of Times Won') +
-  ggtitle('Figure 6',
-          subtitle = "2002 Men's Wimbledon")
+  ggtitle("2019 Men's Wimbledon")
 ```
 
-### Conclusions
+# Conclusions
 
-### Limitations
+# Limitations
 
@@
 
-### Bibliography
+# References

### 2019-12-18 PaperDraft.Rmd
Centered title

@@
 ---
-title: "Tennis"
+title: |
+  | \vspace{3.5in} \LARGE Predicting the Outcomes of Tennis Tournaments
+subtitle: "A Monte Carlo Approach"
 author: "Olivia Beck, Emma Lewis, Ryan Volkert"

### 2019-12-19 PaperDraft.Rmd
Edits

@@
 
-For our report, we replicated the methods outlined in @Tennis for predicting the outcome of a tennis tourement.
+For our report, we replicated the methods outlined in @Tennis for predicting the outcome of a tennis tournament.
+We used the empirical probability of each player winning a rally given they served to calculate theoretical probabilities that the player wins a game, a set, a match, and a tournament given the other players in the tournament.
 
@@
 This assumption has been made in other reports relating to the probability of winning a game in other racket sports and even though serves in tennis are not iid random variables in reality.
-For most purposes this is not an outragous assumption as the divergence from iid is small.
+For most purposes this is not an outrageous assumption as the divergence from iid is small.
 
@@
 
-- P(A Winnning a Set | A Served)
+- P(A Winning a Set | A Served)
 
@@
 
-<!-- Need to add P(winning the Tournement) -->
+- P(Winning the Tournament): Let $\boldsymbol{P}_{ij}$ be the probability that player i wins the match against player j. Then for the 4 semifinalists players i, j, k, and l:
+
+$$p^T_i =  \boldsymbol{P}_{ij}(\boldsymbol{P}_{ik}\boldsymbol{P}_{kl} + \boldsymbol{P}_{il}\boldsymbol{P}_{lk} ) $$
+Note that $\sum_{\forall i} p^T_i =1$. We will sample 1 player from the 4 semifinalists with the probabilities calculated above to determine the tournament winner.
 
@@
 We want to reproduce the probability of winning a game.
-Table 1 compares the empirical probablity of winning a game versus the theoretical probability of winning a game calculated in @Tennis verus the probability of winning a game that we calculated for the 4 semi finalists in this tournament.
-We can see that the vales that we caluculated and the values calculated in @Tennis are the same.
-These values do differ slightly from the empiricial probabilities.
+Table 1 compares the empirical probability of winning a game versus the theoretical probability of winning a game calculated in @Tennis versus the probability of winning a game that we calculated for the 4 semi finalists in this tournament.
+We can see that the vales that we calculated and the values calculated in @Tennis are the same.
+These values do differ slightly from the empirical probabilities.
 Table 2 outlines the same comparisons except for the men's 2002 US Open.
 
-Next, we want to comapare the probability of winning a tournement.
-@Tennis does not provide their predictions of tournament winners, only their probabilies comparted to what actually happened in the tournement.
-The paper also only considers the 4 semifinalists when predicting the tournement, so we will as well.
+Next, we want to compare the probability of winning a tournament.
+@Tennis does not provide their predictions of tournament winners, only their probabilities compared to what actually happened in the tournament.
+The paper also only considers the 4 semifinalists when predicting the tournament, so we will as well.
 
@@
 
-We fist look at 2002 US Open's Womens tournement for the 4 semi finalists.
-We calculate the probability each semi finalist has of winning the tournament, then we sample one player to win the tournament with the probabilites we calculated.
-Figure 1 shows the results from 2000 tournements played with these 4 semi finalists.
-From our simlations we predict that S.
-Williams wins the tournement, and in fact she did win this tournement.
+We fist look at 2002 US Open's Women's tournament for the 4 semi finalists.
+We calculate the probability each semi finalist has of winning the tournament, then we sample one player to win the tournament with the probabilities we calculated.
+Figure 1 shows the results from 2000 tournaments played with these 4 semi finalists.
+From our simulations we predict that S.
+Williams wins the tournament, and in fact she did win this tournament.
 
@@
 Using the same method outline above, we can see in Figure 2 that we predict P.
-Sampras to win the tournement, and in fact he did win this tournament.
+Sampras to win the tournament, and in fact he did win this tournament.
 
@@
 
-Next, we consider data from the 2002 Wimbeldon.
+Next, we consider data from the 2002 Wimbledon.
 The probability of winning a rally for the 4 semifinalists for both women's and men's can be found in Table 3.
@@
 Halep actually won the 2019 Women's Wimbledon.
-Similarly, in Figure 6 we predict that Rodger Federer and Rafeal Nadal essentially have an equal probability of winning the tournement, but it was Novak Djokovic who actually won the tournement.
-Again, the discrepencies between who won the tourment and what we predicted are discussed in the limitations section.
+Similarly, in Figure 6 we predict that Rodger Federer and Rafeal Nadal essentially have an equal probability of winning the tournament, but it was Novak Djokovic who actually won the tournament.
+Again, the discrepancies between who won the tournament and what we predicted are discussed in the limitations section.
 ```{r, echo =FALSE, warning=FALSE, fig.pos="H", message=FALSE}
@@
 
+Overall, we were able to predict the winner of a tennis tournament from the 4 semi finalists with relative accuracy using monte carlo methods.
+We used the empirical probabilities of winning a rally on serve going into a tournament to calculate the probability of the 4 semi finalists winning the tournament.
+The discrepancies between our predictions and the actual winners of the tournament can be contributed to the fact that we assumed all rallies are iid, when in reality, this is not the case.
+This will be addressed further in the limitations section.
+
 # Limitations

### 2019-12-19 PaperDraft.Rmd
Edits

@@
 
-$$p^T_i =  \boldsymbol{P}_{ij}(\boldsymbol{P}_{ik}\boldsymbol{P}_{kl} + \boldsymbol{P}_{il}\boldsymbol{P}_{lk} ) $$
-Note that $\sum_{\forall i} p^T_i =1$. We will sample 1 player from the 4 semifinalists with the probabilities calculated above to determine the tournament winner.
+$$p^{TC}_i =  \boldsymbol{P}_{ij}(\boldsymbol{P}_{ik}\boldsymbol{P}_{kl} + \boldsymbol{P}_{il}\boldsymbol{P}_{lk} ) $$
+Note that $\sum_{\forall i} p^{TC}_i =1$. We will sample one  player from the 4 semifinalists with the probabilities calculated above to determine the tournament winner.
 

### 2019-12-20 FinalPaper.Rmd
Some more edits

--- 2019-12-19 PaperDraft.Rmd
@@
 output: pdf_document
-header - input: 
-  - \usepackage{float}
 bibliography: bibliography.bib
@@
 library(tidyverse)
+opts_chunk$set(fig.pos = 'H')
 set.seed(400)
@@
 
-For our report, we replicated the methods outlined in @Tennis for predicting the outcome of a tennis tournament.
-We used the empirical probability of each player winning a rally given they served to calculate theoretical probabilities that the player wins a game, a set, a match, and a tournament given the other players in the tournament.
+This report replicates the methods outlined by @Tennis for predicting the outcome of a tennis tournament.
+We used the empirical probability of each player winning a rally given they served to calculate theoretical probabilities that the player wins a game, a set, a match, and a tournament.
+We first used the same data that @Tennis used for the 2002 Wimbledon and US Open tournaments.
+Our report then expands on the original study by doing the same analysis for the 2019 Wimbledon tournament.
 
@@
 
-The probability of winning a game, a set, and a match in tennis are calculated based on the each players probability of winning a point on a serve.
-This paper and the reference paper,@Tennis both make the assumption that each serve is an independently and identically distributed (iid) random variable.
-This assumption has been made in other reports relating to the probability of winning a game in other racket sports and even though serves in tennis are not iid random variables in reality.
-For most purposes this is not an outrageous assumption as the divergence from iid is small.
+The probability of winning a game, a set, and a match in tennis are calculated based on each player's probability of winning a point on a serve.
+This paper and the reference paper both make the assumption that each serve is an independently and identically distributed (iid) random variable.
+This assumption has been made in reports relating to the probability of winning a game in other racket sports.
+It is important to note that serves in tennis are not iid random variables in reality.
+For most purposes this the divergence from iid is small, so we ignore the dependency.
 
 A game in tennis is played with one player serving and is won by the first player to score four or more points and to be at least two points ahead of the other player.
-Player A can win a game against player B by a score of (4,0), (4,1) or (4,2), or else the score becomes (3,3) which is called "deuce".
+Player A can win a game against Player B by a score of (4,0), (4,1) or (4,2), or else the score becomes (3,3) which is called "deuce".
 
@@
 
-To win a match a player in woman's format a player must win two out of three sets and in men's format a player must win three out of five sets.
+To win a match in the women's format, a player must win two out of three sets and three out of five in the men's format.
 
@@
 
-Data for the 2002 Wimbledon for men's and women's as well as 2002 US Open for men's and women's was provided in @Tennis. Data for 2019 Wimbledon for men's and women's was found at @2019data.
+Data for the 2002 tournaments was provided by @Tennis. Data for the 2019 Wimbledon for was found at @2019data.
 
@@
 
- $$p_A^R = \frac{\text{Points Won On Serve}}{\text{Points Served}}$$
+\begin{equation}
+p_A^R = \frac{\text{Points Won On Serve}}{\text{Points Served}}
+\end{equation}
 
@@
 
-$$p_A^G = (p_A^R)^4[1+4q_A^R+10(q_A^R)^2] +20(p_A^Rq_A^R)^3(p_A^R)^2[1-2p_A^Rq_A^R]^{-1}$$
+\begin{equation}
+p_A^G = (p_A^R)^4[1+4q_A^R+10(q_A^R)^2] +20(p_A^Rq_A^R)^3(p_A^R)^2[1-2p_A^Rq_A^R]^{-1}
+\end{equation}
 
@@
 
-$$p_A^S =\sum_{j=0}^4p_A^S(6,j) + p_A^S(7,5) + p_A^S(6,6)p_A^T$$
+\begin{equation}
+p_A^S =\sum_{j=0}^4p_A^S(6,j) + p_A^S(7,5) + p_A^S(6,6)p_A^T
+\end{equation}
 
-- P(A Winning the Tie Breaker | A Served Initially)
-
-$$p_A^T = \sum_{j=0}^5p_A^T(7,j) +  p_A^T(6,6)p_A^Rq_B^R[1 - p_A^Rp_B^R - q_A^Rq_B^R]^{-1}$$
-
-- P(Winning a Women's Match, Best of 3)
-
-$$p_A^M = (p_A^S)^2 + 2(p_A^S)^2p_B^S$$
-
-- P(Winning a Men's Match, Best of 5)
-
-$$p_A^M = (p_A^S)^3 + 3(p_A^S)^3p_B^S + 6(p_A^S)^3(p_B^S)^2$$
-
-- P(Winning the Tournament): Let $\boldsymbol{P}_{ij}$ be the probability that player i wins the match against player j. Then for the 4 semifinalists players i, j, k, and l:
-
-$$p^{TC}_i =  \boldsymbol{P}_{ij}(\boldsymbol{P}_{ik}\boldsymbol{P}_{kl} + \boldsymbol{P}_{il}\boldsymbol{P}_{lk} ) $$
-Note that $\sum_{\forall i} p^{TC}_i =1$. We will sample one  player from the 4 semifinalists with the probabilities calculated above to determine the tournament winner.
-
-Where, $p_A^S(i,j)$ is defined recursively as:
+$p_A^S(i,j)$ is defined recursively as:
 
@@
 
-And,  $p_A^T(i,j)$ is defined recursively as:
+- P(A Winning the Tie Breaker | A Served Initially)
+
+\begin{equation}
+p_A^T = \sum_{j=0}^5p_A^T(7,j) +  p_A^T(6,6)p_A^Rq_B^R[1 - p_A^Rp_B^R - q_A^Rq_B^R]^{-1}
+\end{equation}
+
+$p_A^T(i,j)$ is defined recursively as:
 
@@
 
-# Reproducability
+- P(Winning a Women's Match, Best of 3)
 
-First we will consider data from the 2002 US Open for both men's and women's.
+\begin{equation}
+p_A^M = (p_A^S)^2 + 2(p_A^S)^2p_B^S
+\end{equation}
+
+- P(Winning a Men's Match, Best of 5)
+
+\begin{equation}
+p_A^M = (p_A^S)^3 + 3(p_A^S)^3p_B^S + 6(p_A^S)^3(p_B^S)^2
+\end{equation}
+
+- P(Winning the Tournament): Let $\boldsymbol{P}_{ij}$ be the probability that player i wins the match against player j. Then for the 4 semifinalists players i, j, k, and l:
+
+\begin{equation}
+p^{TC}_i =  \boldsymbol{P}_{ij}(\boldsymbol{P}_{ik}\boldsymbol{P}_{kl} + \boldsymbol{P}_{il}\boldsymbol{P}_{lk} )
+\end{equation}
+
+Note that $\sum_{\forall i} p^{TC}_i =1$. We will sample one player from the 4 semifinalists with the probabilities calculated above to determine the tournament winner.
+
+# Reproducibility
+
+First we will consider data from the 2002 US Open for both the men's and women's tournaments.
 We want to reproduce the probability of winning a game.
-Table 1 compares the empirical probability of winning a game versus the theoretical probability of winning a game calculated in @Tennis versus the probability of winning a game that we calculated for the 4 semi finalists in this tournament.
-We can see that the vales that we calculated and the values calculated in @Tennis are the same.
+Tables 1 and 2 compare the empirical probability of winning a game to the theoretical probability of winning a game calculated by @Tennis and the probability that we calculated for the four semi-finalists in each tournament.
+We can see that the values that we calculated and the values calculated by @Tennis are the same.
 These values do differ slightly from the empirical probabilities.
-Table 2 outlines the same comparisons except for the men's 2002 US Open.
 
-Next, we want to compare the probability of winning a tournament.
-@Tennis does not provide their predictions of tournament winners, only their probabilities compared to what actually happened in the tournament.
-The paper also only considers the 4 semifinalists when predicting the tournament, so we will as well.
+Next, we want to check the probability of winning a tournament.
+@Tennis do not provide their predictions of tournament winners.
+They also only consider the four semi-semifinalists in each tournament, so we will as well.
 
-```{r, echo = FALSE, fig.pos="H"}
+```{r, echo = FALSE}
 
@@
 
-kable(TDWomen, format = "latex", booktabs = TRUE, caption = "Data for the Womens Semifinalists in the 2002 U.S. Open Tournament
+kable(TDWomen, format = "latex", booktabs = TRUE, caption = "Data for the Women's Semifinalists in the 2002 U.S. Open Tournament
 ")%>%
@@
 
-```{r, echo = FALSE, fig.pos="H"}
+```{r, echo = FALSE}
 
@@
 
-kable(TDMen, format = "latex", booktabs = TRUE, caption = "Data for the Mens Semifinalists in the 2002 U.S. Open Tournament
+kable(TDMen, format = "latex", booktabs = TRUE, caption = "Data for the Men's Semifinalists in the 2002 U.S. Open Tournament
 ")%>%
@@
 
-```{r, echo=FALSE, message=F, warning=F, fig.pos="H", fig.cap = "2002 Women's US Open"}
+```{r, echo=FALSE, message=F, warning=F, fig.cap = "2002 US Open", fig.show = 'hold', out.width = "50%"}
 W02 <- read_csv('2002 US Open tournament- Women.csv') %>%
@@
   xlab("Players") + 
-  ylab("Number of Times Won") +
+  ylab("Proportion of Times Won") +
   ggtitle("2002 Women's US Open")
 
-```
-
-We fist look at 2002 US Open's Women's tournament for the 4 semi finalists.
-We calculate the probability each semi finalist has of winning the tournament, then we sample one player to win the tournament with the probabilities we calculated.
-Figure 1 shows the results from 2000 tournaments played with these 4 semi finalists.
-From our simulations we predict that S.
-Williams wins the tournament, and in fact she did win this tournament.
-
-Similarly, we want to consider the 2002 US Open for the men's semifinalists.
-Using the same method outline above, we can see in Figure 2 that we predict P.
-Sampras to win the tournament, and in fact he did win this tournament.
-
-```{r, echo=FALSE, message=FALSE, warning=FALSE, fig.pos="H", fig.cap = "2002 Men's US Open"}
 mOpen <- read_csv('2002 US Open- Men.csv') %>%
@@
   ggtitle("2002 Men's US Open")
-
 ```
 
-Next, we consider data from the 2002 Wimbledon.
-The probability of winning a rally for the 4 semifinalists for both women's and men's can be found in Table 3.
-Figure 3 shows the results for the 2002 Women's Wimbledon.
-We predict that V.
-Williams wins, but in reality S.
-Williams had an upset win.
-Some speculations as to why we predicted incorrectly can be found in the Limitations section.
-Figure 4 shows the same methods as Figure 3, but for the men's semi finalists.
-We predict L.
-Hewitt to win the tournament, and in fact he does.
+We first look at the 2002 US Open.
+We calculated the probability each semi-finalist has of winning the tournament, then randomly sampled one player to win calculated weights.
+We repeated this 2,000 times, and took the player with the most sampled wins to be the predicted winner.
+Figure 1 shows the results from this method for the men's and women's tournaments.
+Our simulations predict that Serena Williams wins the women's tournament, and Pete Sampras wins the men's tournament.
+These results are consistent with the outcome of the actual 2002 US Open.
 
-```{r, echo = FALSE, fig.pos="H"}
+The 2002 Wimbledon is considered below.
+
+```{r, echo = FALSE}
 
@@
 ```
-```{r, message=F, warning=F, fig.pos="H", fig.cap = "2002 Women's Wimbledon"}
+```{r, message=F, warning=F, fig.cap = "2002 Wimbledon", fig.show = 'hold', out.width = "50%"}
 wWim02 <- read_csv('2002 Wimbledon -Women.csv') %>%
@@
   ggtitle("2002 Women's Wimbledon")
-```
-```{r, message=F, warning=F, fig.pos="H", fig.cap = "2002 Men's Wimbledon"}
+
 mWim02 <- read_csv('2002 Wimbledon- Men.csv') %>%
@@
 
+The probability of winning a rally for the four semifinalists for both women's and men's can be found in Table 3.
+Figure 2 shows the results of our method.
+We predict that Venus Williams wins, but in reality Serena Williams had an upset win.
+Some speculations as to why we predicted incorrectly can be found in the limitations section.
+For the men's semi finalists, we predict L.
+Hewitt to win the tournament, and in fact he does.
+
 # Extension
@@
 Again, the discrepancies between who won the tournament and what we predicted are discussed in the limitations section.
-```{r, echo =FALSE, warning=FALSE, fig.pos="H", message=FALSE}
+
+```{r, echo=F, warning=FALSE, message=FALSE}
 #Women
@@
 Tab<-cbind(Tab1, Tab2)
+
 kable(Tab, format = "latex", booktabs = TRUE, caption = "Data for the Semifinalists in the 2019 Wimbledon Tournament
@@
           kable_styling(full_width = T)
-
 ```
-
-```{r, warning=FALSE, echo=FALSE, message=F, fig.pos="H", fig.cap = "2019 Women's Wimbledon"}
-
+```{r, warning=FALSE, echo=FALSE, message=F, fig.cap = "2019 Wimbledon", fig.show = 'hold', out.width = "50%"}
 T4 <- table(base::sample(wWim19$Name, 2000, prob = wWim19$pTC, replace = TRUE))
@@
   ggtitle("2019 Women's Wimbledon")
-```
-
-```{r, warning=FALSE, echo=FALSE, message=F, fig.pos="H", fig.cap = "2019 Men's Wimbledon"}
 
@@
 
+\newpage
 # References

### 2019-12-20 ps.R

@@ -1,23 +1,0 @@
-
-pga <- 0.5
-qga <- 1- pga
-
-pgb <- 0.5
-qga <- 1-pgb
-
-a.1 <- (pga*qgb)^3
-a.2 <- 3*pga^3
-
-
-
-
-
-ps<-
-
-
-
-a.5 <- 60 * (pga)^3 * qg1^2 * pg2^2 * qg2^3 +
-  40 * pga^2 * qg1^3 * pg2 * qg2^4 +
-  20 * pga^4 * qg1 * pg2^3 * qg2^2 +
-  5 * pga * qg1^4 * qg2^5 +
-  pga^5 * pg2^4 * qg2
